### 2023-06-08 paper/main.tex
first_commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Local Wave Field Synthesis by Temporal Bandlimitation*
\thanks{This work was supported by the János Bolyai Research Scholarship of the Hungarian Academy of Sciences, the ÚNKP-22-5-BME-318 New National Excellence Program of the Ministry for Innovation and Technology from the source of the National Research, Development and Innovation Fund
and by the OTKA PD-143129 and OTKA K-143436 grants.
}
}

\author{\IEEEauthorblockN{Gergely Firtha}
\IEEEauthorblockA{\textit{Dept. of Networked Systems and Services} \\
\textit{Budapest University of Technologies and Economics}\\
H-1111 Budapest, Hungary \\
firtha@hit.bme.hu}
\and
\IEEEauthorblockN{Nara Hahn}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{Frank Schultz}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{Péter Fiala}
\IEEEauthorblockA{\textit{Dept. of Networked Systems and Services} \\
\textit{Budapest University of Technologies and Economics}\\
H-1111 Budapest, Hungary \\
fiala@hit.bme.hu}
}

\maketitle

\begin{abstract}
    Wave Field Synthesis (WFS) aims at the reproduction of a desired target wavefront by driving an ideally continuous loudspeaker distribution with properly chosen secondary source driving signals.
    In practical applications, using a discrete set of loudspeakers degrades the accuracy of reproduction heavily due to the violation of the theoretical requirements.
    As a result, spatial aliasing wavefronts emerge from the individual loudspeaker elements in addition to the intended virtual wavefront, perceived as strong colouration above the so-called spatial aliasing frequency.
    Local Wave Field Synthesis (LWFS) approaches improve the reproduction accuracy over a limited listening area by allowing stronger artefacts outside the control region.
    The present contribution discusses a novel LWFS approach, relying on the transformation of spatially defined antialiasing filters into an equivalent temporal filter bank.
    The resulting antialiased driving functions ensure aliasing-free synthesis at a predefined listening position at the cost of temporally bandlimited sound field at other listening regions.
    The results of the proposed approach are compared with a recent LWFS approach employing direct spatial bandlimitation.
\end{abstract}

\begin{IEEEkeywords}
Wave Field Synthesis, LWFS, Spatial antialiasing
\end{IEEEkeywords}

\section{Introduction}

\section*{Acknowledgment}

This work was supported by the János Bolyai Research Scholarship of the Hungarian Academy of Sciences, the ÚNKP-22-5-BME-318 New National Excellence Program of the Ministry for Innovation and Technology from the source of the National Research, Development and Innovation Fund
and by the OTKA PD-143129 and OTKA K-143436 grants.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2023-06-09 paper/main.tex
paper_started

@@
 \usepackage{xcolor}
+
+\input{scidefs}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
+\section{Theoretical basics}
+\subsection{The local propagation vector:}
+Consider an arbitrary steady-state free space sound field at an angular frequency $\omega$.
+As a standard ansatz in the field of geometrical acoustics the sound field can be written in the general polar from as 
+\begin{equation}
+P(\vx,\omega) = A^P(\vx) \te^{- \ti \omega \phi^P(\vx)},
+\label{eq:Pxw}
+\end{equation}
+where $A^P(\vx)$ and $\phi^P(\vx)$ are real-valued functions. 
+This formulation applies to both plane waves and (3D) point sources.
+The propagation dynamics of the sound field are governed by its phase function $\phi^P(\vx)$, termed as the eikonal in the field of ray acoustics.
+In the temporal domain, the sound field can be obtained by taking the inverse Fourier transform of \eqref{eq:Pxw}, yielding:
+\begin{equation}
+p(\vx,t) = A^P(\vx) \, \delta \! \left( t - \phi^P(\vx)\right).
+\end{equation}
+From the above formulation it is evident that the eikonal $\phi^P(\vx)$ describes the propagation delay the wavefront takes to arrive at $\vx$.
+The eikonal equation is obtained by substituting the ansatz \eqref{eq:Pxw} into the Helmholtz equation, stating that in a source free volume 
+\begin{equation}
+    \left| \nabla \phi^P(\vx) \right| = \frac{1}{c}
+\end{equation}
+is fulfiled.
+The gradient of the eikonal is termed as the local propagation vector 
+\begin{equation}
+    \hat{\vk}^P(\vx) = \posvec{3}{\hat{k}_x^P(\vx)}{\hat{k}_y^P(\vx)}{\hat{k}_z^P(\vx)} = c \nabla_{\! \vx} \phi^P(\vx,\omega).
+\end{equation}
+In steady-state, the local propagation vector is perpendicular to the wavefront (equiphase positions) at an arbitrary location with unit length pointing towards the local propagation direction \cite{Firtha2016}.
+In the temporal domain it points into the local propagation direction at the time instant of the wavefront passby.
+
+%For simplicity, in the followings we assume that all the involved fields propagate horizontally in the plane of investigation, i.e. $\hat{k}_z^P(x,y,0) = 0$.
+
+\subsection{2.5D Wave Field Synthesis:}
+Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D Green's function.
+In this geometry the target field inside the area bounded by the SSD is described by the  Kirchhoff approximation of 2.5D Kirchhoff-Helmholtz integral, from which the 2.5D driving functions can be extracted.
+For an arbitrary simple target virtual sound field $P(\vxo,\omega)$ the steady-state driving functions read as \cite{Firtha2016}
+\begin{equation}
+D(\vxo,\omega) = \underbrace{\sqrt{8\pi \frac{\ti \omega}{c}}}_{ H_{\text{pre}}(\omega) }
+w(\vxo) \sqrt{d_{\mathrm{ref}}(\vxo)}
+ P(\vxo,\omega)
+\label{Eq:WFS25D}
+\end{equation}
+The driving function consists of 
+\begin{itemize}
+    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$ 
+    \item a secondary source selection window 
+    \begin{equation}
+        w(\vxo) = \max{\left( \hat{k}_{\mathrm{n}}^P(\vxo),0\right)}, 
+    \end{equation}
+    where $\hat{k}_{\mathrm{n}}^P(\vxo)$ is the normal component of the local propagation vector 
+    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (c.f. \cite{Firtha2016})
+    \item the virtual field measured on the SSD.
+\end{itemize}
+Assuming a simple virtual sound field as given by \eqref{eq:Pxw} the driving functions can be written 
+\begin{equation}
+    D(\vxo,\omega) = H_{\text{pre}}(\omega)
+    \underbrace{ w(\vxo)  \, \sqrt{d_{\mathrm{ref}}(\vxo)} \, A^P(\vxo) }_{A^D(\vxo)} \te^{- \ti \omega \phi^P(\vxo)}
+\end{equation}    
+and in the time domain as
+\begin{equation}
+d(\vxo,t) = h_{\text{pre}}(t) \ast_t  A^D(\vxo)\,  \delta\left( t - \phi^P(\vxo)\right),
+\label{eq:d_wfs_td}
+\end{equation}
+with $A^D(\vxo)$ being the real valued overall gain factor of the driving function, $\ast_t$ denoting temporal convolution and $h_{\text{pre}}(t)$ is the temporal WFS prefilter impulse response.
+For an analyitcal FIR pre-equalization filter implementation the reader is referred to \cite{Schultz2016}.
+In the following due to the associativity of convolution this prefiltering is excluded from the discussion.
+
+\subsection{Aliasing artifacts in WFS}
+
 \section*{Acknowledgment}
@@
 
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
+\bibliographystyle{unsrt}
+\bibliography{dissertation}
 \vspace{12pt}

### 2023-06-11 paper/main.tex
..

@@
 \usepackage{xcolor}
+\usepackage{overpic,subfigure, tikz}
 
@@
 
-\subsection{2.5D Wave Field Synthesis:}
+\subsection{Conventional 2.5D Wave Field Synthesis}
 Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D Green's function.
@@
 
+\begin{figure*}[h!]
+    \begin{center}
+    \begin{overpic}[width = 0.75\columnwidth]{figs/ideal_synthesis.png}
+        \footnotesize \put(0,2){(a)}
+    \end{overpic} \hspace{2cm}
+    \begin{overpic}[width = 0.75\columnwidth]{figs/aliased_synthesis.png}
+        \footnotesize \put(0,2){(b)}
+    \end{overpic}
+    \\
+    \begin{overpic}[width = 0.75\columnwidth]{figs/ideal_synthesis_spectrum.png}
+        \footnotesize \put(0,0){(c)}
+    \end{overpic} \hspace{2cm}
+    \begin{overpic}[width = 0.75\columnwidth]{figs/aliased_synthesis_spectrum.png}
+        \footnotesize \put(0,0){(d)}
+    \end{overpic}
+\end{center}
+    \caption{fg}
+\label{Fig:aliasing}
+\end{figure*}
+Conventional WFS theory assume a continuous secondary source distribution.
+In practical applications the SSD is composed of evenly spaced discrete source elements.
+As a result, \emph{aliasing wavefronts} emerge from the individual secondary sources, following the intended virtual wavefront, leading to a \emph{spatial aliasing phenomena}.
+Alisaing is perceived as strong colouration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occuring predominantly above the \emph{aliasing frequency}.
+
+Figure \ref{Fig:aliasing} illustrates spatial aliasing in the temporal domain through the example of the synthesis of an impulsive plane wave, arriving from $\phi_{\mathrm{PW}} = 0^{\circ}$, applying a discrete secondary source distribution in comparement with a quasi-continuous synthesis scenario.
+In the current example the SSD is a circular one with the radius of $R_0 = 2~\mathrm{m}$, consisting of $N_0 = 90$ 3D point sources.
+The aliased synthesis in the temporal domain is depicted in Figure \ref{Fig:aliasing} (b).
+
+Mathematically, aliasing can be modeled as the discretization of the theoretically continuous driving functions:
+Assume that a suitable parametrization of the secondary source is given by $d(s,t)$ is given e.g.
+the arc length $s = R\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
+The discretization process is given by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas in the actual secondary source positions:
+\begin{equation}
+    d_s(s,t) = \sum_{\nu = 0}^{N_0} d(s,t) \, \delta(s - \nu \Delta s),
+    \label{eq:sampling_td}
+\end{equation}
+where $\Delta s$ is the sampling arc length.
+
+By investigating the sampling process in the frequency-wavenumber domain, the spectrum of the sampled driving function is given by
+\begin{equation}
+    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}(k_s- \nu \frac{2\pi}{\Delta s},\omega),
+    \label{eq:sampling_fd}
+\end{equation}
+where $t \rightarrow \omega$ and $s \rightarrow k_s$ are Fourier-transform pairs.
+Obviously, for a closed SSD contour the spatial Fourier-transform yields a discrete spectrum, consisting non-zero components only on the multiples of $\frac{1}{R_0}$ (i.e. a Fourier series).
+In the followings the spatial spectrum refers to the distribution of the non-zero spectral/wavenumber values, and the corresponding wavenumber refers to the spatial frequency of the harmonic basis functions, measured along the closed curve.
+Figure \ref{Fig:aliasing} (c) and (d) illustrate the quasi-continuous and the sampled driving function's spectra.
+
+From \eqref{eq:sampling_fd} it can be concluded that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber $k_{s, \mathrm{s}} \frac{2\pi}{\Delta s}$.
+Since the conventional driving functions are not-bandlimited, therefore, the repeating spectra will overlap above the Nyquist wavenumber $k_{s, \mathrm{Nyq}} = \frac{\pi}{\Delta s}$, for which the corresponding angular frequency is the aliasing frequency of the discretization scheme, as depicted in \ref{Fig:aliasing} (d).
+
+Obviously, spatial aliasing can be avoided by analytically spatial-bandlimiting the driving functions to the Nyquist wavenumber.
+This can be performed by either spatially filtering the driving functions with an appropriate spatial low-pass filter prior to numerical evaluation, or performing bandlimitation directly in the wavenumber (modal) domain analytically.
+The latter approach is implemented by \cite{Nara and Fiete}, and will serve as a reference solution in the following investigation.
+However, the modal bandlimitation solution is available only for plane wave and point source virtual source models synthesized by a circular SSD, at the cost of increased computational complexity.
+
+In the following an alternative, approximate solution is presented, allowing spatial antialiasing filtering for an arbitrary virtual source model and arbitrary SSD contour, performed by FIR filtering in the temporal domain.
+The technique relies on an analytical transform of spatially defined antialiasing filters to an equivalent temporal domain filter bank.
+
+\section{Time domain antialiasing filter design}
+
+\subsection{Spatial to temporal filter transform}
+First, a general transfromation is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
+
+Assume an arbitrary filter impulse response defined in the spatial domain, denoted by $h_x(s)$.
+Again, $s$ is a suitable parametrization of the SSD contour.
+The spatially filtered driving function is obtained from the convolution of the conventional driving functions and the filter impulse response along the SSD contour
+\begin{equation}
+    d'_x(s,t) = h_x(s) \ast_x d(s,t) = \int h_x(s-s_0) \, d(s_0,t) \, \td s_0,
+    \label{eq:spatial_conv}
+\end{equation}
+where $\ast_x$ denotes a circular convolution for a convex SSD contour or a linear convolution in case of an infinite long linear SSD.
+
+Let's assume a temporal filter impulse response, defined for each SSD element $h_t(s,t)$.
+The temporally filtered driving functions are obtained from the temporal convolution of each SSD elements' driving function by the corresponding temporal impulse response
+\begin{equation}
+    d'_t(s,t) = h_t(s,t) \ast_t d(s,t) = \int_{-\infty}^{\infty} h_t(s,t-t_0) \, d(s,t_0) \, \td t_0.
+    \label{eq:temp_conv}
+\end{equation}
+Our aim is to express the temporal filter bank $h_t(s,t)$ in terms of the spatial filter, so that the result of the temporal convolution \eqref{eq:temp_conv} coincides with the spatial filtering result \eqref{eq:spatial_conv}, i.e.
+\begin{equation}
+    d'_x(s,t) = d'_t(s,t)
+\end{equation}
+holds.
+
+The following transformation is allowed by the spatio-temporal structures of the conventional driving functions \eqref{eq:d_wfs_td}, in which the spatial and temporal dimensions are interconnected in the argument of a Dirac-delta, due to the wave propagation characteristics.
+Again, in the following the pre-equalization filter is omitted from discussion, since equalization filtering can be performed following the antialiasing process.
+
+The temporal convolution in \eqref{eq:temp_conv} can be evaluated by substituting the general WFS driving function \eqref{eq:d_wfs_td} and exploiting the sifting property of the Dirac-delta, yielding
+\begin{equation}
+    d'_t(s,t) = A^D(s) \, h_t \!\left(s,t- \phi^P(s) \right).
+\end{equation}
+With applying a time shift of $\frac{1}{c} \phi^P(s)$ to both sides the temporal filter impulse response is connected with the spatial convolution as
+{\footnotesize
+\begin{multline}
+    h_t\left(s,t\right) = \frac{1}{A^D(s)}\int h_x(s-s_0) \, d\left(s_0,t+ \frac{1}{c} \phi^P(s) \right) \, \td s_0 = \\
+    \frac{1}{A^D(s)} \, \int h_x(s-s_0) \, A^D(s_0) \delta\left( t + \frac{1}{c} \left(  \phi^P(s) - \phi^P(s_0) \right)\right) \td s_0.
+\end{multline}}
+To evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd}, which states that
+\begin{equation}
+\int f(s_0) \delta(g(s_0)) \td s_0 = \sum_i \frac{f(s_i)}{| \frac{\partial}{\partial s_0} g(s_0) |_{s = s_i}}, \hspace{3mm} g(s_i) = 0.
+\end{equation}
+In the present problem the zeros of the Dirac's argument are found where         
+\begin{equation}
+    \frac{\phi^P(s_i) }{c} = t + \frac{\phi^P(s)}{c}
+    \label{eq:zero}
+\end{equation}
+is satisfied.
+In the following it is assumed that a single zero $s_i$ exists, satisfying \eqref{eq:zero}.
+This assumption means that the wavefront arrives at each SSD element at a unique time instant, being strictly true for a virtual plane wave and a linear SSD.
+With this assumption and by utilizing that 
+\begin{equation}
+    \frac{\partial}{\partial s_0} g(s_0) = -\frac{1}{c} \frac{\partial}{\partial s_0} \phi^P(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
+\end{equation}
+i.e. the derivative of the phase function is the tangential component of the local propagation vector, the integral can be evaluated.
+The resulting general transformation relation between the spatial and temporal filters are given as
+\begin{equation}
+    h_t\left(s,t\right) = \frac{A^D(s_i)}{A^D(s)} \, \frac{ c }{|\hat{k}_t^P(s_i)|} h_x(s-s_i).
+\end{equation}
+
 \section*{Acknowledgment}

### 2023-06-11 Derivation/derivation.tex
derivation_added

\documentclass[12pt,a4paper]{article}

\newcommand{\note}[1]{{\color{red}#1}}
%
\usepackage{layouts}
\usepackage{amsmath,bm}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx,overpic,subfigure}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows}
\usepackage{booktabs} 			% Nice tables
\usepackage{csquotes}			% Quotation
\usepackage{multirow} 			% Multirow cells in tables
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage[small,bf]{caption}
\usepackage{ae,aecompl}
\usepackage{url}
\usepackage[american]{babel}
\usepackage{hyperref}
\usepackage{nomencl}
\usepackage[toc,page]{appendix}
\usepackage{amssymb}
\usepackage{steinmetz}
\usepackage{palatino}
\usepackage{array}
\usepackage{booktabs}
\usepackage{footnote}
\usepackage{multicol}
%

\input{mydefs}
%
\title{Transforming spatial filters to time domain filters for sound field synthesis driving functions}
\date{\today \\
Budapest University of Technology and Economics, \\ Dept. of Networked Systems and Services, \\ Laboratory of Acoustics and Studio Technologies}
\author{Firtha Gergely}

\begin{document}
\maketitle

\subsection{General form of driving functions}

\begin{figure}[b!]
	\centering
	\begin{overpic}[width = .7\columnwidth ]{figs/general_sfs.png}
	\small
	\put(0,26){virtual source}
	\put(44.5,0.5){$\mathbf{0}$}
	\put(71,31){$\vx$}
	\put(39,21){$\vni$}
	\put(43,15){$\vxo$}
	\begin{turn}{27}
	\put(57,-3){$|\vx - \vxo|$}
	\end{turn}
	\put(50,35){$\Omega$}
	\put(80,20.5){$\dO$}
	\end{overpic}
	\caption{Geometry for the general sound field synthesis problem}
	\label{Fig:Theory:general_sfs_geometry}
\end{figure}

Assume a general 2.5D or 3D sound field synthesis (SFS) problem, as depicted for the 2.5D case in Figure \ref{Fig:Theory:general_sfs_geometry}.
The virtual source is assumed to be either a 3D plane wave or the field of a point source.
Generally, such a steady state 3D sound field can be written as
\begin{equation}
P(\omega,\vx) = A^P(\vx) \, \te^{-\ti  \omega \phi^P(\vx) } 
\end{equation}
while in the time domain reading as
\begin{equation}
    p(t,\vx) = A^P(\vx) \, \delta( t -  \phi^P(\vx) ).
\end{equation}
The phase function is related to the normalized local wavenumber vector as
\begin{equation}
    \frac{1}{c} \hat{k}^P(\vx) =  \nabla_{\vx} \, \phi^P(\vx) .
\end{equation}

The driving function that synthesises the virtual field with the secondary source distribution is given by
\begin{itemize}
    \item for a 3D SFS scenario:
     \begin{equation}
        D(\omega, \vxo) = 2 \ti \, w(\vxo) \, \frac{\omega}{c} \, \hat{\kn^P}(\vxo) \, P(\omega,\vxo) 
     \end{equation}
    \item for a 2.5D SFS scenario:
    \begin{equation}
        D(\vxo, \omega) = w(\vxo) \,
        \sqrt{ \frac{8\pi \ti \omega}{c} } \, \sqrt{\dref(\vxo)} \,
        \hat{\kn^P} (\vxo)\, P(\vxo,\omega),
     \end{equation}
\end{itemize}
In both cases the driving functions can be written in the general form of 
\begin{equation}
    D(\omega, \vxo) = A(\vxo) \, \te^{-\ti \omega \phi^P(\vxo) },
 \end{equation}
 prefiltered with a filter $H(\omega) \sim \ti \omega$ in the 3D and $H(\omega) \sim \sqrt{\ti \omega}$ in the 2.5D case, with also $A(\vx)$ depending on the dimensionality of the problem.
 Hence--similarly to the virtual field formulation-- the driving function in the time domain reads as
 \begin{equation}
   d(t, \vxo) = A(\vxo) \, \delta( t-  \phi^P(\vxo) ).
   \label{eq:general_driv_fun}
 \end{equation}

\subsection{Problem statement}

The spatial filtering of the driving functions is a frequently emerging question in numerous applications.
The direct application of real-time spatial filtering may, however, be computationally expensive.
This section disscusses how spatial convolutional filter can be transformed into temporal filtering by exploiting the nature of the driving functions, discussed for 2.5D synthesis case.

Assume a spatial impulse response given by $h_x(x)$.
The spatially filtered driving function is given in the time domain as 
\begin{equation}
    d'_x(t,\vxo) = \int h_x(\vxo - \vx_1) \, d(t, \vx_1) \, \td \vx_1 
    \label{eq:d_filt}
\end{equation}

Since the actual form of the driving function interconnect the spatial and temporal positions: i.e. on each spatial location the temporal shape of the driving function is identical (apart from an amplitude variation), therefore, it is possible to derive a temporal filter impulse response, performing identical filtering as given by \eqref{eq:d_filt}.
In the followings the identical temporal filter is derived

\subsection{Derivation}
Assume that a temporal impulse response $h_t(t,\vxo)$ can be formulated so that the spatially filtered driving functions are identical with the temporally filtered driving functions, i.e. 
\begin{equation}
    d'_x(t,\vxo)  = \int h_x(\vxo - \vx_1) \, d(t, \vx_1) \, \td \vx_1 = \int h_t(t - t_0,\vxo) \, d(t_0, \vxo) \, \td t_0  = d'_t(t,\vxo) 
\end{equation}
hold.
Let's substitute the assumed, simple form of the general driving functions given by \eqref{eq:general_driv_fun} to each sides resulting in
\begin{equation}
    \int h_x(\vxo - \vx_1) \, 
    A(\vx_1) \, \delta( t-  \phi^P(\vx_1) )
    \, \td \vx_1 =  A(\vxo)  \int h_t(t - t_0,\vxo)
    \, \delta( t_0 - \phi^P(\vxo) ) \, \td t_0.
\end{equation}
On the right side the sifting property of the Dirac-delta can be exploited directly:
\begin{equation}
    \int h_x(\vxo - \vx_1) \, 
    A(\vx_1) \, \delta( t-  \phi^P(\vx_1) )
    \, \td \vx_1 = A(\vxo)  h_t(t - \phi^P(\vxo) , \vxo) 
\end{equation}
i.e. the (shifted) temporal filter impulse response is given by
\begin{equation}
    h_t(t -  \phi^P(\vxo) , \vxo)  = \frac{1}{ A(\vxo) }
    \int h_x(\vxo - \vx_1) \, 
    A(\vx_1) \, \delta( t-  \phi^P(\vx_1) )
    \, \td \vx_1 
\end{equation}
For the sake of simplicity let's apply a temporal shift of $+\phi^P(\vxo)$, resulting in
\begin{equation}
    h_t(t, \vxo)  = \frac{1}{ A(\vxo) }
    \int h_x(\vxo - \vx_1) \, 
    A(\vx_1) \, \delta( t + \phi^P(\vxo)- \phi^P(\vx_1) )
    \, \td \vx_1 
\end{equation}

\vspace{1cm}
The spatial convolution can be evaluated by exploiting the generalized sifting property of the Dirac-delta
\begin{equation}
    \int_{-\infty}^{\infty} f(x) \, \delta(g(x)) \, \td x = \sum_{i} \frac{f(x_i)}{\left| \frac{\partial}{\partial x} g(x) \right|_{x = x_i}}, \hspace{5mm} \text{where} \hspace{5mm} g(x_i) = 0.
\end{equation}
or in terms of contour integration as
\begin{equation}
    \int f(\vx_1) \, \delta(g(\vx_1)) \, \td \vx_1 = \sum_{i} \frac{f(\vx_i)}{\left| \nabla_{\vx_1} \, g(\vx_1) \cdot \vv(\vx_1) \right|_{\vx_1 = \vx_i}}, \hspace{5mm} \text{where} \hspace{5mm} g(\vx_i) = 0.
\end{equation}
In the current scenario 
\begin{align}
    g(\vx_1) &= t + \phi^P(\vxo)- \phi^P(\vx_1) \\
    \nabla_{\vx_1} g(\vx_1) &= - \frac{1}{c}  \hat{\vk}^P(\vx_1) \\
    f(\vx_1)  &= h_x(\vxo - \vx_1) \,  A(\vx_1)
\end{align}
For sake of simplicity it is assumed that a single zero position for the Dirac-argument exists, given where
\begin{equation}
     \phi^P(\vx_i) = t + \phi^P(\vxo)
\end{equation}
is satisfied. 
The physical interpretation of this assumption is discussed later.

By denoting the time dependent zero-position as $\vx_i(t)$ the integral simplifies to 
\begin{equation}
    h_t(t, \vxo)  = \frac{A(\vx_i(t)) }{ A(\vxo) }  \,
    \frac{c}{| \hat{k_\mathrm{v}}^P(\vx_i(t))  |} \,
     h_x(\vxo - \vx_i(t))
\end{equation}
with $\hat{k_\mathrm{v}}^P$ denoting the tangential component of the normalized (time independent) local wavenumber vector

\subsection{Linear SSD, plane wave}
For a plane wave the phase function is given as
\begin{equation}
     \phi^P(\vx) = \frac{1}{c} (\hat{k_x} x + \hat{k_y} y),
\end{equation}
furthermore, let's assume a linear SSD with direction vector $\vv = [v_x, \, v_y]$, hence both $\vxo$ and $\vx_i$ satisfy
\begin{align}
    0 &= -v_y x_0 + v_x y_0 + c,\\
    0 &= -v_y  x_i + v_x y_i + c,\\
    0 &= -v_y (x_i-x_0) + v_x (y_i-y_0),\\
    y_i-y_0 &= \frac{v_y}{v_x} (x_i-x_0)\\
    x_i-x_0 &= \frac{v_x}{v_y} (y_i-y_0).
\end{align}
Hence, indeed, for a plane wave arriving at a linear SSD a single solution exists for the above system of equation as long as the plane wave does not arrive normally to the SSD (this latter case will be further examined later):
For a given $\vxo$, position $\vx_i$ is found, where
\begin{equation}
    \hat{k_x} x_i + \hat{k_y} y_i = t c + \hat{k_x} x_0 + \hat{k_y} y_0
\end{equation}
\begin{equation}
    \hat{k_x} (x_i-x_0) + \hat{k_y} (y_i-y_0) = t c
\end{equation}

\begin{equation}
    x_i = x_0 + v_x\frac{t c}{\hat{k_x}v_x+ \hat{k_y} v_y } 
\end{equation}
\begin{equation}
    y_i = y_0 + v_y\frac{t c}{\hat{k_x} v_x  + \hat{k_y}v_y} 
\end{equation}
It can be realized that $\hat{k_x} v_x  + \hat{k_y}v_y = \vv \cdot \hat{\vk^P} = \hat{k_v^P}$, i.e. by vector notation
\begin{equation}
    \vx_i = \vxo + \vv \frac{t c}{\hat{k_v^P}} 
\end{equation}
And the filter impulse response reads as
\begin{equation}
    h_t(t, \vxo)  = \frac{A( \vxo + \vv \frac{t c}{\hat{k_v^P}}) }{ A(\vxo) }  \,
    \frac{c}{| \hat{k_\mathrm{v}}^P( \vxo + \vv \frac{t c}{\hat{k_v^P}})  |} \,
     h_x(-\vv \frac{t c}{\hat{k_v^P}})
\end{equation}
In the followings the following assumptions are made:
\begin{itemize}
    \item it is assumed that the spatial filter impulse response is relatively short, and the amplitude factor of the driving function changes slowly in the proximity of $\vxo$, i.e.
$A( \vxo + \vv \frac{t c}{\hat{k_v^P}}) \approx A(\vxo)$.
    \item it is assumed that the incident field is locally plane at $\vxo$, i.e. again, in the proximity of $\vxo$ $\hat{k_\mathrm{v}}^P( \vxo + \vv \frac{t c}{\hat{k_v^P}}) \approx  \hat{k_\mathrm{v}}^P( \vxo)$ holds.
\end{itemize}
Similarly to standard WFS assumptions, the assumptions hold for SSD elements with small curvature and for virtual field with small local curvature (plane waves and far-field of point sources). 
Finally it is exploited that usually the spatial filter impulse reponses are defined as the function of a single parameter, i.e. the vector notation in the function's argument is redunant.
With all these considerations the connection between the spatial filter and the corresponding temporal filter at a single SSD element at $\vxo$ is given by 
\begin{equation}
    h_t(t, \vxo)  = \frac{c}{\left| \hat{k_\mathrm{v}^P}( \vxo ) \right| } \,
     h_x(-t \frac{c}{\hat{k_v^P}(\vxo)}).
\end{equation}
Hence, the temporal impulse response is obtained by rescaling the spatial impulse response.

\vspace{3mm}
The above formulation allows the interconnection of the spatial filter transfer function with the corresponding temporal filter frequency characteristics as well.

Assume that the transfer function of the spatial filter is given by $H_x(k_x)$.
The corresponding temporal filter transfer is obtained simply from the scaling property of the Fourier transformed
\begin{equation}
    \frac{1}{2\pi}\int h_t(t, \vxo) \te^{-\ti \omega t} \td t  = \frac{c}{\left| \hat{k_\mathrm{v}^P}( \vxo ) \right| } \frac{1}{2\pi} \int 
     h_x(-t \frac{c}{\hat{k_v^P}(\vxo)}) \te^{-\ti \omega t} \td t
\end{equation}
\begin{equation}
 H_t(\omega, \vxo) =  H_x( -\omega\frac{\hat{k_v^P}(\vxo)}{c}) 
\end{equation}

\subsection{Alternative derivation: stationary position for the wavenumber domain driving functions}
See: Firtha PhD, Appendix D.

\subsection{Application example: antialiasing filtering}

\end{document}

### 2023-06-11 paper/main.tex
derivation_added

@@
 
+\subsubsection{The exact transformation}
 The following transformation is allowed by the spatio-temporal structures of the conventional driving functions \eqref{eq:d_wfs_td}, in which the spatial and temporal dimensions are interconnected in the argument of a Dirac-delta, due to the wave propagation characteristics.
+The main idea of the deriation is that by exploiting the sifting property of the Dirac-delta in the driving functions both spatial and temporal convolutions \eqref{eq:spatial_conv} and \eqref{eq:temp_conv} can be evaluated, from which the temporal filter impulse responses can be expressed as the function of the spatial one.
 Again, in the following the pre-equalization filter is omitted from discussion, since equalization filtering can be performed following the antialiasing process.
@@
 The temporal convolution in \eqref{eq:temp_conv} can be evaluated by substituting the general WFS driving function \eqref{eq:d_wfs_td} and exploiting the sifting property of the Dirac-delta, yielding
-\begin{equation}
-    d'_t(s,t) = A^D(s) \, h_t \!\left(s,t- \phi^P(s) \right).
-\end{equation}
-With applying a time shift of $\frac{1}{c} \phi^P(s)$ to both sides the temporal filter impulse response is connected with the spatial convolution as
-{\footnotesize
+\begin{align}
+    d'_t(s,t) = A^D(s) \, h_t \!\left(s,t- \phi^P(s) \right) \\
+    d'_t(s,t + \phi^P(s) ) = A^D(s) \, h_t \!\left(s,t\right).
+    \label{eq:temp_conv_eval}
+\end{align}
+For the second equation a time shift of $\phi^P(s)$ was applied for the sake latter simplicity.
+
+The shifted spatially filtered driving function reads as
 \begin{multline}
-    h_t\left(s,t\right) = \frac{1}{A^D(s)}\int h_x(s-s_0) \, d\left(s_0,t+ \frac{1}{c} \phi^P(s) \right) \, \td s_0 = \\
-    \frac{1}{A^D(s)} \, \int h_x(s-s_0) \, A^D(s_0) \delta\left( t + \frac{1}{c} \left(  \phi^P(s) - \phi^P(s_0) \right)\right) \td s_0.
-\end{multline}}
-To evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd}, which states that
+    d'_x(s,t+ \phi^P(s) ) = \int h_x(s-s_0) \, d(s_0,t+ \phi^P(s) ) \, \td s_0 = \\
+    \int h_x(s-s_0) \, A^D(s_0)\, \delta(s_0,t+ \left(\phi^P(s)-\phi^P(s_0)\right)  ) \, \td s_0.
+    \label{eq:spat_conv2}
+\end{multline}
+In order to evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd}, which states that
 \begin{equation}
@@
 \begin{equation}
-    \frac{\phi^P(s_i) }{c} = t + \frac{\phi^P(s)}{c}
+    \phi^P(s_i) = t + \phi^P(s)
     \label{eq:zero}
@@
 This assumption means that the wavefront arrives at each SSD element at a unique time instant, being strictly true for a virtual plane wave and a linear SSD.
-With this assumption and by utilizing that 
+The derivative of the phase function is given by
 \begin{equation}
-    \frac{\partial}{\partial s_0} g(s_0) = -\frac{1}{c} \frac{\partial}{\partial s_0} \phi^P(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
+    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \phi^P(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
 \end{equation}
-i.e. the derivative of the phase function is the tangential component of the local propagation vector, the integral can be evaluated.
-The resulting general transformation relation between the spatial and temporal filters are given as
+i.e. it is the tangential component of the local propagation vector.
+With the above assumptions the integral \eqref{eq:spat_conv2} can be evaluated, yielding
 \begin{equation}
-    h_t\left(s,t\right) = \frac{A^D(s_i)}{A^D(s)} \, \frac{ c }{|\hat{k}_t^P(s_i)|} h_x(s-s_i).
+    d'_x(s,t+ \phi^P(s) ) = h_x(s-s_i) \, A^D(s_i)
+    \label{eq:spat_conv_eval}
 \end{equation}
+
+Finally, by combining \eqref{eq:spat_conv_eval} and \eqref{eq:temp_conv_eval} the resulting general transformation relation between the spatial and temporal filters are given as
+\begin{equation}
+    h_t\left(s,t\right) = \frac{A^D(s_i)}{A^D(s)} \, \frac{ c }{|\hat{k}_t^P(s_i)|} h_x(s-s_i),
+\end{equation}
+where $s_i$ satisfies \eqref{eq:zero}.
+
+\subsubsection{Local plane wave approximation}
+The above formulation already allows one to transform an arbitrary spatial impulse response into an equivalent temporal filter for each SSD element, as long as the virtual field model is known and \eqref{eq:zero} can be solved.
+In order to give a more general solution it is assumed that the virtual field is locally plane, being a usual high frequency assumption in WFS theory. 
+As a further general WFS assumption it is supposed that the SSD is locally plane.
+These requirements inherently ensure that a single solution exists for \eqref{eq:zero}\footnote{Except for a plane wave arriving normally to the SSD, at which case the temporal filter is transformed into a Dirac-delta.}.
+With these assumptions the phase function is given as
+\begin{equation}
+\phi^P(\vx) = \hat{k}^P_x(\vx)x +  \hat{k}^P_y(\vx) y 
+\end{equation}
+and \eqref{eq:zero} is satisfied where 
+\begin{equation}
+    s_i = s + \frac{c \cdot t}{\hat{k}_t^P(s)}
+\end{equation}
+Finally, as a crucial approximation it is assumed that both the amplitude of the driving function and the propagation vector varies slowly along the SSD, i.e $A^D(s_i) \approx A^D(s)$ and $\hat{k}_t^P(s_i) \approx \hat{k}_t^P(s)$ holds.
+With these assumptions the corresponding filter transform reads as
+\begin{equation}
+    h_t\left(s,t\right) =\frac{ c }{|\hat{k}_t^P(s)|} h_x\left(-t \,\frac{c}{\hat{k}_t^P(s)}\right).
+    \label{eq:temporal_transform}
+\end{equation}
+
+Equation \eqref{eq:temporal_transform} can be directly expressed in the spectral domain by taking the Fourier transform of both sides, relating the frequency response of the spatial and the temporal filters.
+By denoting $\mathcal{F}\left( h_x(s)\right) = H_x(k_s)$ the corresponding transform is given by
+\begin{equation}
+    H_t\left(s,\omega\right) = H_x\left(-\frac{\omega}{c}\hat{k}_t^P(s)\right) = H_x\left(-k_t^P(s)\right),
+    \label{eq:frequency_transform}
+\end{equation}
+where $k_t^P(s)$ is the tangential component of the local wavenumber vector, being a vector in a steady state sound field, pointing in the local propagation direction with the length being $\omega/c$ \cite{Firtha2019phd}.
+Hence, as the main result of the present discussion, the temporal filter transfer can be obtained from the wavenumber (modal) content of the spatial filter by simple rescaling in terms of the local wavenumber vector.
 

### 2023-06-12 paper/main.tex
figs_added

@@
 
+The validity and the error analysis of the above filter transform was investigated in details in \cite{Firtha DAGA2023}.
+In the following the direct application for Local WFS is discussed.
+
+\subsection{Application for Local Wave Field Synthesis}
+
+From Figure \ref{Fig:aliasing} (d) it is obvious, that the overlapping of the sampled driving function spectra, and, therefore, the presence of aliasing waves can be avoided by spatially bandlimiting the driving functions to the Nyquist wavenumber prior to sampling.
+Spatial bandlimitation can be easily performed by designing a suitable spatial antialiasing filter and transform it into an equivalent temporal filter bank, based on the results of the previous section.
+An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensure analytical spatial bandlimitation.
+
+The avoiding of the spectral overlapping can be achieved by bandlimiting the driving function to the sampling wavenumber $k_{s,\mathrm{s}} = \frac{2\pi}{\Delta s}$, with either simmatrically to $k_s = 0$ or choosing an arbitrary central wavenumber $k_{s,0}$.
+First the former case is investigated in details.
+
+\subsubsection{Symmetrical antialiasing}
+As the most simple antialiasing strategy, the spectral overlapping is avoided by the spatial lowpass filtering of the driving functions to the Nyquist wavenumber, $k_{s,\mathrm{Nyq}} = \frac{\pi}{\Delta s}$
+
+The effect of symmetrical bandlimitation is demonstrated via the exemplary low pass filter chosen to be an $N$-th order Butterworth design, defined in the wavenumber domain as
+\begin{equation}
+    H_x(k_s) = \frac{ 1 }{ \sqrt{ 1 + \left( k_s / k_{s,\mathrm{Nyq}} \right)^{2N} } }.
+\end{equation}
+
+From the transform given by \eqref{eq:frequency_transform} the angular frequency response of the equivalent temporal filter bank is given by
+\begin{equation}
+    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \omega\frac{\hat{k}_t^P(s)}{c k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c}  \right)^{2N} } } .
+\end{equation}
+with 
+\begin{equation}
+    \omega_c = c \frac{k_{s,\mathrm{Nyq}}}{\hat{k}_t^P(s)} = c\frac{ \pi}{\Delta s} \frac{1}{\hat{k}_t^P(s)}.
+    \label{eq:cutoff_fr}
+\end{equation}
+Therefore, the cut-off frequency of the equivalent low-pass filter on a given SSD element is directly determined by the tangential component of the local propagation vector.
+
+The result of antialiasing filtering is depicted in Figure \ref{Fig:symm_antialiasing} for the synthesis scenario discussed in the foregoing.
+Figure (a) shows the result of the synthesis, while Figure (b) illustrates the spectrum of the bandlimited, sampled driving functions.
+\begin{figure}[h!]
+    \begin{center}
+    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis.png}
+        \footnotesize \put(0,2){(a)}
+    \end{overpic} 
+    \\
+    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_spectrum.png}
+        \footnotesize \put(0,0){(b)}
+    \end{overpic}
+\end{center}
+    \caption{Symmetric antialiasing filtering}
+\label{Fig:symm_antialiasing}
+\end{figure}
+It is highlighted, that
+
+It should be noted that the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach:
+in the aspect of antialiasing filtering SSD positions where the local wanumber vector is higher than the Nyquist wanumber are highly attenuated, with the window width decreasing with increasing angular frequency.
+\begin{figure}[]
+\begin{overpic}[width = 1\columnwidth]{figs/equivalent_windows.png}
+\end{overpic} 
+\caption{Illustration of equivalent frequency dependent window functions}
+\label{Fig:equivalent_windows}
+\end{figure}
+The actual shape of the spatial windows are given by the wavenumber spectrum of the spatial lowpass filter $H_x(k_s)$, rescaled in terms of the local wavenumber vector.
+The set of window functions applied in the present simulation scenario are illustrated in Figure \ref{Fig:equivalent_windows}.
+
+\subsubsection{Non-symmetrical antialiasing}
+
+\begin{figure}[h!]
+    \begin{center}
+    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_steered.png}
+        \footnotesize \put(0,2){(a)}
+    \end{overpic} 
+    \\
+    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_spectrum_steered.png}
+        \footnotesize \put(0,0){(b)}
+    \end{overpic}
+\end{center}
+    \caption{Non-symmetric antialiasing filtering}
+\label{Fig:symm_antialiasing}
+\end{figure}
 \section*{Acknowledgment}

### 2023-06-12 paper/main.tex
figs_added

@@
 \end{figure}
-It is highlighted, that
+It is highlighted, that the presented antialiasing strategy ensures highly suppressed aliasing waves in the center of the circular source array.
+In other positions of the listening area lateral aliasing wavefronts remain in the reproduced wave field, while the target, virtual wave front is bandlimited.
+This phenomena can be easily understood by investigating the synthesis scenario in a geometrical manner:
+
+From \eqref{eq:cutoff_fr} it is clear that since the antialiasing filter cutoff frequency is proportional with the tangential component of the virtual field on the SSD, therefore, in a circualr array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
+This fullband SSD element is marked with white dot in Figure \ref{Fig:symm_antialiasing} (a).
+From general WFS theory it is known that the fullband SSD element will dominate the synthesized wavefront (i.e.
+will serve as a stationary SSD position) for spatial positions along a straight line crossing through the actual SSD element into the direction of the local propagation vector.
+Therefore, the present antialiasing strategy ensures aliasing-free synthesis along a straight line for which the fullband SSD element is the stationary secondary source. 
+The direction of the line of aliasing-free synthesis is marked with a dashed arrow in the figure.
+This is in contrast with conventional Local WFS approaches, in which the synthesis is optimized in the proximity of a pre-defined reference position over a circular area.
 
@@
 \end{figure}
+
+It is important to emphasize that if no actual SSD element exists for a given plane wave direction (for which the wave arrives perpendicularly) then all the SSD elements are bandlimited, i.e.
+
 \section*{Acknowledgment}

### 2023-06-12 paper/main.tex
figs_added

@@
 \begin{equation}
-    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \omega\frac{\hat{k}_t^P(s)}{c k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c}  \right)^{2N} } } .
+    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{c}\frac{\hat{k}_t^P(s)}{k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c(s)}  \right)^{2N} } } .
 \end{equation}
@@
 \begin{equation}
-    \omega_c = c \frac{k_{s,\mathrm{Nyq}}}{\hat{k}_t^P(s)} = c\frac{ \pi}{\Delta s} \frac{1}{\hat{k}_t^P(s)}.
+    \omega_c(s) = c \frac{k_{s,\mathrm{Nyq}}}{\hat{k}_t^P(s)} = c\frac{ \pi}{\Delta s} \frac{1}{\hat{k}_t^P(s)}.
     \label{eq:cutoff_fr}
@@
 \subsubsection{Non-symmetrical antialiasing}
+As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial pass-band filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = k_{s,\mathrm{Nyq}}$.
+
+Again, the concept is illustrated via a simple synthesis scenraio as discussed in the foregoing.
+In the present case the spatial bandpass filter is derived by shifting the $N$-th order low-pass Butterworth design to the center wavenumber $k_{s,0}$
+\begin{equation}
+    H_x(k_s) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{k_s-k_{s,0}}{k_{s,\mathrm{Nyq}} }\right)^{2N} } }.
+\end{equation}
+Again, an equivalent filter bank is derived by using the transform \eqref{eq:frequency_transform}, resulting in the frequency response of 
+\begin{equation}
+    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{c}\frac{\hat{k}_t^P(s) - k_{s,0}}{k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c(s)}  \right)^{2N} } } .
+\end{equation}
+with 
+\begin{equation}
+    \omega_c(s) = c \frac{k_{s,\mathrm{Nyq}}}{\hat{k}_t^P(s)- k_{s,0}} = c\frac{ \pi}{\Delta s} \frac{1}{\hat{k}_t^P(s)- k_{s,0}}.
+\end{equation}
 

### 2023-06-12 paper/main.tex
figs_added

@@
 Again, the concept is illustrated via a simple synthesis scenraio as discussed in the foregoing.
-In the present case the spatial bandpass filter is derived by shifting the $N$-th order low-pass Butterworth design to the center wavenumber $k_{s,0}$
+In the present case the spatial bandpass filter is derived by shifting the $N$-th order low-pass Butterworth design to the a frequency dependent center wavenumber $k_{s,0}(\omega) = \frac{\omega}{c} \hat{k}_{s,0}$ (where $\hat{k}_{s,0}$ is a constant normalized wavenumber value)
 \begin{equation}
-    H_x(k_s) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{k_s-k_{s,0}}{k_{s,\mathrm{Nyq}} }\right)^{2N} } }.
+    H_x(k_s, \omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{k_s-k_{s,0}(\omega)}{k_{s,\mathrm{Nyq}} }\right)^{2N} } }.
 \end{equation}
+Note, that in this case even the spatial filters are frequency dependent.
+This seemingly pointless assumption ensures later that the transformed temporal filters remain time-invariant.
+
 Again, an equivalent filter bank is derived by using the transform \eqref{eq:frequency_transform}, resulting in the frequency response of 
 \begin{equation}
-    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{c}\frac{\hat{k}_t^P(s) - k_{s,0}}{k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c(s)}  \right)^{2N} } } .
+    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{c}\frac{\hat{k}_t^P(s) - \hat{k}_{s,0}}{k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c(s)}  \right)^{2N} } } .
 \end{equation}
-with 
+where $\hat{k}_{s,0}$ is the normalized center wavenumber and with
 \begin{equation}
-    \omega_c(s) = c \frac{k_{s,\mathrm{Nyq}}}{\hat{k}_t^P(s)- k_{s,0}} = c\frac{ \pi}{\Delta s} \frac{1}{\hat{k}_t^P(s)- k_{s,0}}.
+    \omega_c(s) = c \frac{k_{s,\mathrm{Nyq}}}{\hat{k}_t^P(s) - \hat{k}_{s,0}} = c\frac{ \pi}{\Delta s} \frac{1}{\hat{k}_t^P(s) - \hat{k}_{s,0}}.
+    \label{eq:cutoff_asymm}
 \end{equation}
@@
     \caption{Non-symmetric antialiasing filtering}
-\label{Fig:symm_antialiasing}
+\label{Fig:assymm_antialiasing}
 \end{figure}
+The application of the above formulation with an arbitrarily chosen center wavenumber $\hat{k}_{s,0} = 0.5$ is depicted in Figure \ref{Fig:assymm_antialiasing}.
+Note that the wavenumber content of the original spatial lowpass filter is ,,steered'', so that the center frequency varies linearly with the angular freuquency and the slope of the variation is given by the normalized center wavenumber.
+Obviously, this ,,steered'', frequency dependent band-pass filter theoretically also ensures non-overlapping spectra after the discretization process.
+
+From \eqref{eq:cutoff_asymm} it is apparent that in the present case the nearly fullband SSD element will be that, where the tangential local propagation vector coincides with the normalized center wavenumber, i.e.
+where $\hat{k}_t^P(s) = \hat{k}_{s,0} = 0.5$.
+Again, the fullband SSD element is denoted by white dot in Figure \ref{Fig:assymm_antialiasing} (a).
+Similarly to the previous case, this fullband SSD element serves as the stationary SSD position for a set of positions located along a straight line passing through the SSD element with the direction given by this element's local propagation vector.
+The direction along which fullband synthesis is ensured is denoted by dashed arrow in Figure \ref{Fig:assymm_antialiasing} (a).
 
 It is important to emphasize that if no actual SSD element exists for a given plane wave direction (for which the wave arrives perpendicularly) then all the SSD elements are bandlimited, i.e.
+in the synthesized field no fullband synthesis positions will be present.
+Therefore, for a given receiver position the bandwidth of the reproduced field will depend on the virtual source position/virtual plane wave direction and the loudspeaker spacing.
+This phenomena will have a clearly audible effect in case of dynamic WFS scenarios (e.g. moving virtual sources) and the possibilities to overcome this limitation is the topic of future research.
+
+\subsubsection{Application for Local Wave Field Synthesis}
+The findings of the previous subsections can be straightforwardly used in order to apply the above theory directly for Local Wave Field Synthesis.
+In this case a reference position $\vxref$ is prescribed inside the SSD, at which aliasing-free, amplitude and phase correct synthesis has to be ensured.
+
+Amplitude correct synthesis may be achieved by a suitably chosen reference function in \eqref{Eq:WFS25D}, based on the virtual field model.
+For a detailed treatise on the definition of the reference function the reader is referred to \cite{Firtha2019phd}.
+
+On the other hand, aliasing components can be suppressed by ,,steering'' the direction of antialiased synthesis to cross the prescribed reference point.
+This can be performed by finding the stationary position on the SSD for the reference position and choosing the normalized center wavenumber in \eqref{eq:cutoff_asymm} to coincide with the local propagation vector of the stationary position.
+Mathematically, this can be formulated as follows.
+Given a reference position $\vxref$ and an SSD located along $\vxo$, the stationary SSD element $\vxo^*$ satisfies
+\begin{equation}
+    \frac{\vxref - \vxo^*}{\left| \vxref - \vxo^* \right|} = \hat{\vk}^P(\vxo^*).
+\end{equation}
+Once $\vxo^*$ is found, that center wavenumber in \eqref{eq:cutoff_asymm} is found by
+\begin{equation}
+    \hat{k}_{s,0} = \hat{k}_t^P(\vxo^*).
+\end{equation}
+
+Obviously, symmetrical antialiasing filtering, depicted in Figure \ref{Fig:symm_antialiasing} can be regarded as LWFS with choosing $\vxref = [0, \, 0]^{\mathrm{T}}$,
+while Figure \ref{Fig:assymm_antialiasing}, illustrating asymmetrical filtering was generated by choosing $\vxref = [0, \, 1]^{\mathrm{T}}$.
+In both cases in Figure \ref{Fig:symm_antialiasing} and \ref{Fig:assymm_antialiasing} (a) the reference position is denoted by black cross.
+
+\section{Comparison with direct modal bandlimitation}
 

### 2023-06-13 paper/main.tex
corrections

@@
     In practical applications, using a discrete set of loudspeakers degrades the accuracy of reproduction heavily due to the violation of the theoretical requirements.
-    As a result, spatial aliasing wavefronts emerge from the individual loudspeaker elements in addition to the intended virtual wavefront, perceived as strong colouration above the so-called spatial aliasing frequency.
-    Local Wave Field Synthesis (LWFS) approaches improve the reproduction accuracy over a limited listening area by allowing stronger artefacts outside the control region.
+    As a result, spatial aliasing wavefronts emerge from the individual loudspeaker elements in addition to the intended virtual wavefront, perceived as strong coloration above the so-called spatial aliasing frequency.
+    Local Wave Field Synthesis (LWFS) approaches improve the reproduction accuracy over a limited listening area by allowing stronger artifacts outside the control region.
     The present contribution discusses a novel LWFS approach, relying on the transformation of spatially defined antialiasing filters into an equivalent temporal filter bank.
@@
 As a standard ansatz in the field of geometrical acoustics the sound field can be written in the general polar from as
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $A^P(\vx)$ and $\phi^P(\vx)$ are real-valued functions.
@@
 \end{equation}
-is fulfiled.
+is fulfilled.
 The gradient of the eikonal is termed as the local propagation vector
@@
     P(\vxo,\omega)
+    .
     \label{Eq:WFS25D}
@@
 \begin{itemize}
-    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$ 
+    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$,
     \item a secondary source selection window
@@
           \end{equation}
-    where $\hat{k}_{\mathrm{n}}^P(\vxo)$ is the normal component of the local propagation vector 
-    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (c.f. \cite{Firtha2016})
-    \item the virtual field measured on the SSD.
+          where $\hat{k}_{\mathrm{n}}^P(\vxo)$ is the normal component of the local propagation vector,
+    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (c.f. \cite{Firtha2016}),
+    \item and the virtual field measured on the SSD.
 \end{itemize}
-Assuming a simple virtual sound field as given by \eqref{eq:Pxw} the driving functions can be written 
+Assuming a simple virtual sound field as given by \eqref{eq:Pxw} the driving functions can be written as
 \begin{equation}
@@
     \underbrace{ w(\vxo)  \, \sqrt{d_{\mathrm{ref}}(\vxo)} \, A^P(\vxo) }_{A^D(\vxo)} \te^{- \ti \omega \phi^P(\vxo)}
+    ,
 \end{equation}
@@
 with $A^D(\vxo)$ being the real valued overall gain factor of the driving function, $\ast_t$ denoting temporal convolution and $h_{\text{pre}}(t)$ is the temporal WFS prefilter impulse response.
-For an analyitcal FIR pre-equalization filter implementation the reader is referred to \cite{Schultz2016}.
+For an analytic FIR pre-equalization filter implementation the reader is referred to \cite{Schultz2016}.
 In the following due to the associativity of convolution this prefiltering is excluded from the discussion.
@@
 \end{figure*}
-Conventional WFS theory assume a continuous secondary source distribution.
+Conventional WFS theory assumes a continuous secondary source distribution.
 In practical applications the SSD is composed of evenly spaced discrete source elements.
 As a result, \emph{aliasing wavefronts} emerge from the individual secondary sources, following the intended virtual wavefront, leading to a \emph{spatial aliasing phenomena}.
-Alisaing is perceived as strong colouration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occuring predominantly above the \emph{aliasing frequency}.
+Aliasing is perceived as strong coloration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occurring predominantly above the \emph{aliasing frequency}.
 
@@
 Mathematically, aliasing can be modeled as the discretization of the theoretically continuous driving functions:
-Assume that a suitable parametrization of the secondary source is given by $d(s,t)$ is given e.g.
+Assume that a suitable parametrization $d(s,t)$ of the secondary source is given, e.g.
 the arc length $s = R\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
@@
 \begin{equation}
-    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}(k_s- \nu \frac{2\pi}{\Delta s},\omega),
+    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}\left(k_s- \nu \frac{2\pi}{\Delta s},\omega\right),
     \label{eq:sampling_fd}
@@
 where $t \rightarrow \omega$ and $s \rightarrow k_s$ are Fourier-transform pairs.
-Obviously, for a closed SSD contour the spatial Fourier-transform yields a discrete spectrum, consisting non-zero components only on the multiples of $\frac{1}{R_0}$ (i.e. a Fourier series).
+Obviously, for a closed SSD contour the spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of $\frac{1}{R_0}$ (i.e. a Fourier series).
 In the followings the spatial spectrum refers to the distribution of the non-zero spectral/wavenumber values, and the corresponding wavenumber refers to the spatial frequency of the harmonic basis functions, measured along the closed curve.
@@
 
-From \eqref{eq:sampling_fd} it can be concluded that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber $k_{s, \mathrm{s}} \frac{2\pi}{\Delta s}$.
+From \eqref{eq:sampling_fd} it can be concluded that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber $k_{s, \mathrm{s}} = \frac{2\pi}{\Delta s}$.
 Since the conventional driving functions are not-bandlimited, therefore, the repeating spectra will overlap above the Nyquist wavenumber $k_{s, \mathrm{Nyq}} = \frac{\pi}{\Delta s}$, for which the corresponding angular frequency is the aliasing frequency of the discretization scheme, as depicted in \ref{Fig:aliasing} (d).
@@
 In the following an alternative, approximate solution is presented, allowing spatial antialiasing filtering for an arbitrary virtual source model and arbitrary SSD contour, performed by FIR filtering in the temporal domain.
-The technique relies on an analytical transform of spatially defined antialiasing filters to an equivalent temporal domain filter bank.
+The technique relies on an analytic transform of spatially defined antialiasing filters to an equivalent temporal domain filter bank.
 
@@
 \subsection{Spatial to temporal filter transform}
-First, a general transfromation is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
+First, a general transformation is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
 
@@
 The following transformation is allowed by the spatio-temporal structures of the conventional driving functions \eqref{eq:d_wfs_td}, in which the spatial and temporal dimensions are interconnected in the argument of a Dirac-delta, due to the wave propagation characteristics.
-The main idea of the deriation is that by exploiting the sifting property of the Dirac-delta in the driving functions both spatial and temporal convolutions \eqref{eq:spatial_conv} and \eqref{eq:temp_conv} can be evaluated, from which the temporal filter impulse responses can be expressed as the function of the spatial one.
+The main idea of the derivation is that by exploiting the sifting property of the Dirac-delta in the driving functions, both spatial and temporal convolutions \eqref{eq:spatial_conv} and \eqref{eq:temp_conv} can be evaluated, from which the temporal filter impulse responses can be expressed as the function of the spatial one.
 Again, in the following the pre-equalization filter is omitted from discussion, since equalization filtering can be performed following the antialiasing process.
@@
 \end{align}
-For the second equation a time shift of $\phi^P(s)$ was applied for the sake latter simplicity.
+In the second equation the time shift of $\phi^P(s)$ was applied for the sake of simplicity.
 
@@
     d'_x(s,t+ \phi^P(s) ) = h_x(s-s_i) \, A^D(s_i)
+    .
     \label{eq:spat_conv_eval}
@@
 
-Finally, by combining \eqref{eq:spat_conv_eval} and \eqref{eq:temp_conv_eval} the resulting general transformation relation between the spatial and temporal filters are given as
+Finally, by combining \eqref{eq:spat_conv_eval} and \eqref{eq:temp_conv_eval} the resulting general transformation relation between the spatial and temporal filters is given as
 \begin{equation}
@@
     s_i = s + \frac{c \cdot t}{\hat{k}_t^P(s)}
+    .
 \end{equation}
@@
 From Figure \ref{Fig:aliasing} (d) it is obvious, that the overlapping of the sampled driving function spectra, and, therefore, the presence of aliasing waves can be avoided by spatially bandlimiting the driving functions to the Nyquist wavenumber prior to sampling.
-Spatial bandlimitation can be easily performed by designing a suitable spatial antialiasing filter and transform it into an equivalent temporal filter bank, based on the results of the previous section.
-An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensure analytical spatial bandlimitation.
+Spatial bandlimitation can be easily performed by designing a suitable spatial antialiasing filter and transforming it into an equivalent temporal filter bank, based on the results of the previous section.
+An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensures analytical spatial bandlimitation.
 
-The avoiding of the spectral overlapping can be achieved by bandlimiting the driving function to the sampling wavenumber $k_{s,\mathrm{s}} = \frac{2\pi}{\Delta s}$, with either simmatrically to $k_s = 0$ or choosing an arbitrary central wavenumber $k_{s,0}$.
+Spectral overlapping can be avoided by bandlimiting the driving function to the sampling wavenumber $k_{s,\mathrm{s}} = \frac{2\pi}{\Delta s}$, with either symmetrically to $k_s = 0$ or by choosing an arbitrary central wavenumber $k_{s,0}$.
 First the former case is investigated in details.
@@
 \subsubsection{Symmetrical antialiasing}
-As the most simple antialiasing strategy, the spectral overlapping is avoided by the spatial lowpass filtering of the driving functions to the Nyquist wavenumber, $k_{s,\mathrm{Nyq}} = \frac{\pi}{\Delta s}$
+As the simplest antialiasing strategy, the spectral overlapping is avoided by the spatial lowpass filtering of the driving functions to the Nyquist wavenumber, $k_{s,\mathrm{Nyq}} = \frac{\pi}{\Delta s}$.
 
@@
 
-From \eqref{eq:cutoff_fr} it is clear that since the antialiasing filter cutoff frequency is proportional with the tangential component of the virtual field on the SSD, therefore, in a circualr array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
+From \eqref{eq:cutoff_fr} it is clear that since the antialiasing filter cutoff frequency is proportional to the tangential component of the virtual field on the SSD, therefore, in a circualr array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
 This fullband SSD element is marked with white dot in Figure \ref{Fig:symm_antialiasing} (a).
 From general WFS theory it is known that the fullband SSD element will dominate the synthesized wavefront (i.e.
-will serve as a stationary SSD position) for spatial positions along a straight line crossing through the actual SSD element into the direction of the local propagation vector.
+will serve as a stationary SSD position) for spatial positions along a straight line crossing the actual SSD element into the direction of the local propagation vector.
 Therefore, the present antialiasing strategy ensures aliasing-free synthesis along a straight line for which the fullband SSD element is the stationary secondary source.
@@
 It should be noted that the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach:
-in the aspect of antialiasing filtering SSD positions where the local wanumber vector is higher than the Nyquist wanumber are highly attenuated, with the window width decreasing with increasing angular frequency.
+in the aspect of antialiasing filtering SSD positions where the local wavenumber vector is higher than the Nyquist wavenumber are highly attenuated, with the window width decreasing with increasing angular frequency.
 \begin{figure}[]
@@
 \subsubsection{Non-symmetrical antialiasing}
-As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial pass-band filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = k_{s,\mathrm{Nyq}}$.
+As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial band-pass filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = k_{s,\mathrm{Nyq}}$.
 
-Again, the concept is illustrated via a simple synthesis scenraio as discussed in the foregoing.
+Again, the concept is illustrated via a simple synthesis scenario as discussed in the foregoing.
 In the present case the spatial bandpass filter is derived by shifting the $N$-th order low-pass Butterworth design to the a frequency dependent center wavenumber $k_{s,0}(\omega) = \frac{\omega}{c} \hat{k}_{s,0}$ (where $\hat{k}_{s,0}$ is a constant normalized wavenumber value)
@@
 \begin{equation}
-    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{c}\frac{\hat{k}_t^P(s) - \hat{k}_{s,0}}{k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c(s)}  \right)^{2N} } } .
+    H_t(s,\omega) = \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{c}\frac{\hat{k}_t^P(s) - \hat{k}_{s,0}}{k_{s,\mathrm{Nyq}}}  \right)^{2N} } } =  \frac{ 1 }{ \sqrt{ 1 + \left( \frac{\omega}{\omega_c(s)}  \right)^{2N} } }
+    ,
 \end{equation}
@@
 The application of the above formulation with an arbitrarily chosen center wavenumber $\hat{k}_{s,0} = 0.5$ is depicted in Figure \ref{Fig:assymm_antialiasing}.
-Note that the wavenumber content of the original spatial lowpass filter is ,,steered'', so that the center frequency varies linearly with the angular freuquency and the slope of the variation is given by the normalized center wavenumber.
+Note that the wavenumber content of the original spatial lowpass filter is ,,steered'', so that the center frequency varies linearly with the angular frequency and the slope of the variation is given by the normalized center wavenumber.
 Obviously, this ,,steered'', frequency dependent band-pass filter theoretically also ensures non-overlapping spectra after the discretization process.
@@
 Similarly to the previous case, this fullband SSD element serves as the stationary SSD position for a set of positions located along a straight line passing through the SSD element with the direction given by this element's local propagation vector.
-The direction along which fullband synthesis is ensured is denoted by dashed arrow in Figure \ref{Fig:assymm_antialiasing} (a).
+The direction along which fullband synthesis is ensured is denoted by a dashed arrow in Figure \ref{Fig:assymm_antialiasing} (a).
 
@@
 \end{equation}
-Once $\vxo^*$ is found, that center wavenumber in \eqref{eq:cutoff_asymm} is found by
+Once $\vxo^*$ is found, the center wavenumber in \eqref{eq:cutoff_asymm} is found by
 \begin{equation}
@@
 while Figure \ref{Fig:assymm_antialiasing}, illustrating asymmetrical filtering was generated by choosing $\vxref = [0, \, 1]^{\mathrm{T}}$.
-In both cases in Figure \ref{Fig:symm_antialiasing} and \ref{Fig:assymm_antialiasing} (a) the reference position is denoted by black cross.
+In both cases in Figure \ref{Fig:symm_antialiasing} and \ref{Fig:assymm_antialiasing} (a) the reference position is denoted by a black cross.
 

### 2023-06-13 paper/main.tex
..

--- 2023-06-12 paper/main.tex
@@
 \section{Introduction}
+The aim of sound field synthesis is to reproduce a virtual target sound field over an extended listening area using a densely spaced loudspeaker arrangement, known as the secondary source distribution (SSD).
+By feeding the loudspeakers with specific driving functions, the superposition of sound fields from each SSD element should ideally match the target sound field in the intended receiving area.
+One prominent sound field synthesis method is Wave Field Synthesis (WFS) \cite{Berkhout1993:Acoustic_control_by_WFS, Start1997:phd}.%, which obtains the necessary driving functions from a suitable boundary integral representation of the target sound field.
 
@@
 
+\section{Conclusion}
+
 \section*{Acknowledgment}

### 2023-06-13 paper/main.tex
..

@@
 Assume that a suitable parametrization $d(s,t)$ of the secondary source is given, e.g.
-the arc length $s = R\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
+the arc length $s = R_0\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
 The discretization process is given by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas in the actual secondary source positions:
@@
 \subsubsection{Non-symmetrical antialiasing}
-As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial band-pass filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = k_{s,\mathrm{Nyq}}$.
+As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial band-pass filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = 2 k_{s,\mathrm{Nyq}}$.
 
@@
 \section{Comparison with direct modal bandlimitation}
+Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional LWFS implementations, based on direct modal bandlimitation.
+
+{\color{red} A paragraph from Nara should come here about (Fiete's? and) his LWFS approaches}
 
@@
 \vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2023-06-13 paper/main.tex
..

@@
 
+\begin{figure*}[h!]
+    \begin{center}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center.png}
+            \footnotesize \put(0,2){(a)}
+        \end{overpic} \hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_right.png}
+            \footnotesize \put(0,2){(b)}
+        \end{overpic}\hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_front.png}
+            \footnotesize \put(0,2){(c)}
+        \end{overpic} \hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
+            \footnotesize \put(0,2){(d)}
+        \end{overpic}\\
+        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
+            \footnotesize \put(0,2){(a)}
+        \end{overpic} \hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_right.png}
+            \footnotesize \put(0,2){(b)}
+        \end{overpic}\hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
+            \footnotesize \put(0,2){(c)}
+        \end{overpic} \hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
+            \footnotesize \put(0,2){(d)}
+        \end{overpic}\\
+        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
+            \footnotesize \put(0,2){(a)}
+        \end{overpic} \hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_right.png}
+            \footnotesize \put(0,2){(b)}
+        \end{overpic}\hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
+            \footnotesize \put(0,2){(c)}
+        \end{overpic} \hspace{3mm}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
+            \footnotesize \put(0,2){(d)}
+        \end{overpic}\\
+    \end{center}
+    \caption{fg}
+    \label{Fig:aliasing}
+\end{figure*}
+
 \section{Conclusion}

### 2023-06-13 paper/main.tex
..

@@
 \section{Comparison with direct modal bandlimitation}
-Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional LWFS implementations, based on direct modal bandlimitation.
+Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.
 
-{\color{red} A paragraph from Nara should come here about (Fiete's? and) his LWFS approaches}
+{\color{red} A paragraph from Nara should come here about his LWFS approaches}
 
@@
             \footnotesize \put(0,2){(d)}
-        \end{overpic}\\
+        \end{overpic}\\  \vspace{5mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
-            \footnotesize \put(0,2){(a)}
+            \footnotesize \put(0,2){(e)}
         \end{overpic} \hspace{3mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/nara_right.png}
-            \footnotesize \put(0,2){(b)}
+            \footnotesize \put(0,2){(f)}
         \end{overpic}\hspace{3mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
-            \footnotesize \put(0,2){(c)}
+            \footnotesize \put(0,2){(g)}
         \end{overpic} \hspace{3mm}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
-            \footnotesize \put(0,2){(d)}
-        \end{overpic}\\
+        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
+            \footnotesize \put(0,2){(h)}
+        \end{overpic}\\ \vspace{5mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
-            \footnotesize \put(0,2){(a)}
+            \footnotesize \put(0,2){(i)}
         \end{overpic} \hspace{3mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_right.png}
-            \footnotesize \put(0,2){(b)}
+            \footnotesize \put(0,2){(j)}
         \end{overpic}\hspace{3mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
-            \footnotesize \put(0,2){(c)}
+            \footnotesize \put(0,2){(k)}
         \end{overpic} \hspace{3mm}
         \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
-            \footnotesize \put(0,2){(d)}
+            \footnotesize \put(0,2){(l)}
         \end{overpic}\\

### 2023-06-26 paper/main.tex
..
changes_started_to_be_included

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage[english]{babel}          % für deutsche Dokumente
 \usepackage{cite}
@@
 \begin{equation}
-    P(\vx,\omega) = A^P(\vx) \te^{- \ti \omega \phi^P(\vx)},
+    P(\vx,\omega) = A(\vx) \te^{- \ti \omega \tau(\vx)},
     \label{eq:Pxw}
@@
 %
-where $A^P(\vx)$ and $\phi^P(\vx)$ are real-valued functions.
+where $A(\vx)$ and $\tau(\vx)$ are real-valued functions.
 This formulation applies to both plane waves and (3D) point sources.
-The propagation dynamics of the sound field are governed by its phase function $\phi^P(\vx)$, termed as the eikonal in the field of ray acoustics.
+The propagation dynamics of the sound field are governed by its phase function $\tau(\vx)$, termed as the eikonal in the field of ray acoustics.
 In the temporal domain, the sound field can be obtained by taking the inverse Fourier transform of \eqref{eq:Pxw}, yielding:
 \begin{equation}
-    p(\vx,t) = A^P(\vx) \, \delta \! \left( t - \phi^P(\vx)\right).
+    p(\vx,t) = A(\vx) \, \delta \! \left( t - \tau(\vx)\right).
 \end{equation}
-From the above formulation it is evident that the eikonal $\phi^P(\vx)$ describes the propagation delay the wavefront takes to arrive at $\vx$.
+From the above formulation it is evident that the eikonal $\tau(\vx)$ describes the propagation delay the wavefront takes to arrive at $\vx$.
 The eikonal equation is obtained by substituting the ansatz \eqref{eq:Pxw} into the Helmholtz equation, stating that in a source free volume
 \begin{equation}
-    \left| \nabla \phi^P(\vx) \right| = \frac{1}{c}
+    \left| \nabla \tau(\vx) \right| = \frac{1}{c}
 \end{equation}
@@
 \begin{equation}
-    \hat{\vk}^P(\vx) = \posvec{3}{\hat{k}_x^P(\vx)}{\hat{k}_y^P(\vx)}{\hat{k}_z^P(\vx)} = c \nabla_{\! \vx} \phi^P(\vx,\omega).
+    \hat{\vk}^P(\vx) = \posvec{3}{\hat{k}_x^P(\vx)}{\hat{k}_y^P(\vx)}{\hat{k}_z^P(\vx)} = c \nabla \tau(\vx,\omega).
 \end{equation}
@@
     D(\vxo,\omega) = H_{\text{pre}}(\omega)
-    \underbrace{ w(\vxo)  \, \sqrt{d_{\mathrm{ref}}(\vxo)} \, A^P(\vxo) }_{A^D(\vxo)} \te^{- \ti \omega \phi^P(\vxo)}
+    \underbrace{ w(\vxo)  \, \sqrt{d_{\mathrm{ref}}(\vxo)} \, A(\vxo) }_{A^D(\vxo)} \te^{- \ti \omega \tau(\vxo)}
     ,
@@
 \begin{equation}
-    d(\vxo,t) = h_{\text{pre}}(t) \ast_t  A^D(\vxo)\,  \delta\left( t - \phi^P(\vxo)\right),
+    d(\vxo,t) = h_{\text{pre}}(t) \ast_t  A^D(\vxo)\,  \delta\left( t - \tau(\vxo)\right),
     \label{eq:d_wfs_td}
@@
 As a result, \emph{aliasing wavefronts} emerge from the individual secondary sources, following the intended virtual wavefront, leading to a \emph{spatial aliasing phenomena}.
-Aliasing is perceived as strong coloration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occurring predominantly above the \emph{aliasing frequency}.
+Although localization does not degrade due to the precedence effect, aliasing is perceived as strong coloration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occurring predominantly above the \emph{aliasing frequency}.
 
@@
 \begin{equation}
-    d_s(s,t) = \sum_{\nu = 0}^{N_0} d(s,t) \, \delta(s - \nu \Delta s),
+    d_s(s,t) = \sum_{\nu = 0}^{N_0} d(s,t) \, \delta(s - \nu \Delta s) \, \Delta s,
     \label{eq:sampling_td}
@@
 \begin{equation}
-    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}\left(k_s- \nu \frac{2\pi}{\Delta s},\omega\right),
+    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}\left(k_s- \nu \frac{2\pi}{\Delta s},\omega\right) \Delta s,
     \label{eq:sampling_fd}
@@
 where $t \rightarrow \omega$ and $s \rightarrow k_s$ are Fourier-transform pairs.
-Obviously, for a closed SSD contour the spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of $\frac{1}{R_0}$ (i.e. a Fourier series).
+Obviously, for a closed SSD contour the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial period length, i.e. at
+\begin{equation}
+    k_s = m \frac{ 2 \pi }{R_0},
+\end{equation}
+constituting a Fourier series.
+
 In the followings the spatial spectrum refers to the distribution of the non-zero spectral/wavenumber values, and the corresponding wavenumber refers to the spatial frequency of the harmonic basis functions, measured along the closed curve.
@@
         \end{overpic} \hspace{3mm}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_back.png}
             \footnotesize \put(0,2){(h)}
@@
         \end{overpic} \hspace{3mm}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_back.png}
             \footnotesize \put(0,2){(l)}

### 2023-06-26 paper/main.tex
LWFS based on modal band-limitation
...

@@
 where $t \rightarrow \omega$ and $s \rightarrow k_s$ are Fourier-transform pairs.
-Obviously, for a closed SSD contour the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial period length, i.e. at
+Obviously, for a closed SSD contour the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial wavenumber, i.e. at
 \begin{equation}
-    k_s = m \frac{ 2 \pi }{R_0},
+    k_s = \frac{m}{R_0},
 \end{equation}
@@
 
-In the followings the spatial spectrum refers to the distribution of the non-zero spectral/wavenumber values, and the corresponding wavenumber refers to the spatial frequency of the harmonic basis functions, measured along the closed curve.
+In the followings the spatial spectrum refers to the distribution of the non-zero wavenumber values, and the corresponding wavenumber refers to the spatial frequency of the harmonic basis functions, measured along the closed curve.
 Figure \ref{Fig:aliasing} (c) and (d) illustrate the quasi-continuous and the sampled driving function's spectra.
@@
 
-\section{Time domain antialiasing filter design}
+\section{Time domain antialiasing filter}
 
@@
 \begin{equation}
-    d'_x(s,t) = h_x(s) \ast_x d(s,t) = \int h_x(s-s_0) \, d(s_0,t) \, \td s_0,
+    d'_x(s,t) = h_x(s) \ast_s d(s,t) = \int h_x(s-s_0) \, d(s_0,t) \, \td s_0,
     \label{eq:spatial_conv}
@@
 \begin{align}
-    d'_t(s,t) = A^D(s) \, h_t \!\left(s,t- \phi^P(s) \right) \\
-    d'_t(s,t + \phi^P(s) ) = A^D(s) \, h_t \!\left(s,t\right).
+    d'_t(s,t) = A^D(s) \, h_t \!\left(s,t- \tau(s) \right) \\
+    d'_t(s,t + \tau(s) ) = A^D(s) \, h_t \!\left(s,t\right).
     \label{eq:temp_conv_eval}
 \end{align}
-In the second equation the time shift of $\phi^P(s)$ was applied for the sake of simplicity.
+In the second equation the time shift of $\tau(s)$ was applied for the sake of simplicity.
 
@@
 \begin{multline}
-    d'_x(s,t+ \phi^P(s) ) = \int h_x(s-s_0) \, d(s_0,t+ \phi^P(s) ) \, \td s_0 = \\
-    \int h_x(s-s_0) \, A^D(s_0)\, \delta(s_0,t+ \left(\phi^P(s)-\phi^P(s_0)\right)  ) \, \td s_0.
+    d'_x(s,t+ \tau(s) ) = \int h_x(s-s_0) \, d(s_0,t+ \tau(s) ) \, \td s_0 = \\
+    \int h_x(s-s_0) \, A^D(s_0)\, \delta(s_0,t+ \left(\tau(s)-\tau(s_0)\right)  ) \, \td s_0.
     \label{eq:spat_conv2}
@@
 \begin{equation}
-    \phi^P(s_i) = t + \phi^P(s)
+    \tau(s_i) = t + \tau(s)
     \label{eq:zero}
@@
 \begin{equation}
-    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \phi^P(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
+    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \tau(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
 \end{equation}
@@
 \begin{equation}
-    d'_x(s,t+ \phi^P(s) ) = h_x(s-s_i) \, A^D(s_i)
+    d'_x(s,t+ \tau(s) ) = h_x(s-s_i) \, A^D(s_i)
     .
@@
 \begin{equation}
-    \phi^P(\vx) = \hat{k}^P_x(\vx)x +  \hat{k}^P_y(\vx) y
+    \tau(\vx) = \hat{k}^P_x(\vx)x +  \hat{k}^P_y(\vx) y
 \end{equation}
@@
 
-\subsection{Application for Local Wave Field Synthesis}
+\subsection{Application for antialiasing filtering}
 
@@
 The result of antialiasing filtering is depicted in Figure \ref{Fig:symm_antialiasing} for the synthesis scenario discussed in the foregoing.
+In the present case the sampling arc length is given by $\Delta s = \frac{2 \pi R_0}{N}$, i.e. the space-dependent cut-off frequency reads as\begin{equation}
+    \omega_c(s) = \frac{ N}{ 2 R_0 } \frac{c}{\hat{k}_t^P(s)}.
+\end{equation}
+The antialiasing filters were a 4-th order Butterworth deisgn.
+
 Figure (a) shows the result of the synthesis, while Figure (b) illustrates the spectrum of the bandlimited, sampled driving functions.

### 2023-06-26 paper/lwfs-spl.tex

\ldots
For a direct spatial band-limitation,
the sound field is expanded in terms of cylindrical harmonics with respect to the target position.
The modal bandwidth was limited by truncating the expansion to a finite order.
Based on the analytical expressions of the modal impulse responses,
the LWFS driving functions are implemented as FIR filters in the time domain.
The length of the FIR filters depends on the distance between the secondary source and the target position,
ranging between 273 and 787 taps for the considered scenarios
(excluding the WFS pre-filter).
%
Since this approach is based on time-domain sampling,
the resulting filters exhibit temporal aliasing artifacts,
degrading the accuracy in the frequency domain.
It is, therefore, crucial to attenuate the spectral components beyond the Nyquist limit
before the modal impulse responses are sampled.
An analytical anti-aliasing filtering is performed in the continuous-time domain
by using the 15th-order Lagrange interpolation kernel.
%
Interested readers are referred to \cite{hahn2022cylindrical} for further detail.

### 2023-06-27 paper/main.tex
..

@@
 
-{\color{red} A paragraph from Nara should come here about his LWFS approaches}
+\input{lwfs-spl.tex}
 
@@
         \end{overpic} \hspace{3mm}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_right.png}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_left.png}
             \footnotesize \put(0,2){(f)}
@@
         \end{overpic} \hspace{3mm}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_right.png}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_left.png}
             \footnotesize \put(0,2){(j)}

### 2023-06-28 paper/main.tex
add Schultz affil
..
revision1

@@
     \IEEEauthorblockN{Frank Schultz}
-    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-        \textit{name of organization (of Aff.)}\\
-        City, Country \\
-        email address or ORCID}
+    \IEEEauthorblockA{\textit{Institute of Communications Engineering} \\
+        \textit{University of Rostock}\\
+        18059 Rostock, Germany \\
+        frank.schultz@uni-rostock.de}
     \and
@@
 By feeding the loudspeakers with specific driving functions, the superposition of sound fields from each SSD element should ideally match the target sound field in the intended receiving area.
-One prominent sound field synthesis method is Wave Field Synthesis (WFS) \cite{Berkhout1993:Acoustic_control_by_WFS, Start1997:phd}.%, which obtains the necessary driving functions from a suitable boundary integral representation of the target sound field.
+One prominent sound field synthesis method is Wave Field Synthesis (WFS) \cite{Berkhout1993:Acoustic_control_by_WFS, Start1997:phd}.
+
+As WFS obtains the necessary driving functions from a suitable boundary integral representation of the target sound field, perfect phase correct field-reconstruction could be only achieved by employing a theoretical, continuous secondary source distribution.
+In practical applications the SSD constist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
+This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, heavily degrading the quality of reproduction.
+
+The effect of aliasing can be mitigated by restricting the synthesis to a smaller control region inside the listening area at the cost of permitting stronger aliasing artifacts outside the control region.
+These anti-aliased WFS approaches are commonly referred to as Local Wave Field Synthesis (LWFS).
+Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{}.
+However, due to the high computational demand the real-time application of these LWFS approaches is not straightforward.
+
+The present contribution introduces a novel LWFS approach, relying merely on the temporal bandlimitation of the SSD driving functions.
+The temporal filters, defined uniquely for each SSD elements, are obtained from spatial antialiasing filters by means of an analytical spatial-to-temporal filter transformation, introduced by the current authors in a previous contribution \cite{firtha_daga}.
+Similarly to other LWFS techniques, the presented approach ensures aliasing-free synthesis at a predefined listening position at the cost of temporally bandlimited sound field at other listening regions.
+The results of the proposed approach are compared with a conventional LWFS approach employing direct spatial bandlimitation.
 
@@
 \end{equation}
-In steady-state, the local propagation vector is perpendicular to the wavefront (equiphase positions) at an arbitrary location with unit length pointing towards the local propagation direction \cite{Firtha2016}.
+In steady-state, the local propagation vector is perpendicular to the wavefront (equiphase positions) at an arbitrary location of unit length pointing towards the local propagation direction \cite{Firtha2016}.
 In the temporal domain it points into the local propagation direction at the time instant of the wavefront passby.
@@
 \subsection{Conventional 2.5D Wave Field Synthesis}
-Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D Green's function.
+Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D freefield Green's function.
 In this geometry the target field inside the area bounded by the SSD is described by the  Kirchhoff approximation of 2.5D Kirchhoff-Helmholtz integral, from which the 2.5D driving functions can be extracted.
@@
 with $A^D(\vxo)$ being the real valued overall gain factor of the driving function, $\ast_t$ denoting temporal convolution and $h_{\text{pre}}(t)$ is the temporal WFS prefilter impulse response.
-For an analytic FIR pre-equalization filter implementation the reader is referred to \cite{Schultz2016}.
+The analytical pre-equalization filter impulse response is given in \cite{Deregowski1983, Firtha2019phd}, while for an ideal FIR filter implementation the reader is referred to \cite{Schultz2016}.
 In the following due to the associativity of convolution this prefiltering is excluded from the discussion.
@@
     \end{center}
-    \caption{fg}
+    \caption{The synthesized field and the spatial spectrum of the driving function in case of ideal, quasi-continuous SSD (a) and (c), and in case of a discretized SSD (b) and (d).
+    It is important ot note that the spatial spectrum depicts only the non-zero Fourier components (i.e. the Fourier series coefficients) normalized to the sampling wavenumber.}
     \label{Fig:aliasing}
@@
 
-Figure \ref{Fig:aliasing} illustrates spatial aliasing in the temporal domain through the example of the synthesis of an impulsive plane wave, arriving from $\phi_{\mathrm{PW}} = 0^{\circ}$, applying a discrete secondary source distribution in comparement with a quasi-continuous synthesis scenario.
+Figure \ref{Fig:aliasing} illustrates spatial aliasing in the temporal domain through the example of the synthesis of an impulsive plane wave, arriving from $\phi_{\mathrm{PW}} = 0^{\circ}$, applying a discrete secondary source distribution in comparison with a quasi-continuous synthesis scenario.
 In the current example the SSD is a circular one with the radius of $R_0 = 2~\mathrm{m}$, consisting of $N_0 = 90$ 3D point sources.
@@
 \begin{equation}
-    d_s(s,t) = \sum_{\nu = 0}^{N_0} d(s,t) \, \delta(s - \nu \Delta s) \, \Delta s,
+    d_s(s,t) = \sum_{\nu = 0}^{N_0-1} d(s,t) \, \delta(s - \nu \Delta s) \, \Delta s,
     \label{eq:sampling_td}
@@
 where $t \rightarrow \omega$ and $s \rightarrow k_s$ are Fourier-transform pairs.
-Obviously, for a closed SSD contour the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial wavenumber, i.e. at
+Obviously, for a closed SSD contour (most notablz for a circular SSD) the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial wavenumber, i.e.
+at
 \begin{equation}
@@
 
-Obviously, spatial aliasing can be avoided by analytically spatial-bandlimiting the driving functions to the Nyquist wavenumber.
+According to the sampling theorem, spatial aliasing can be avoided by analytically spatial-bandlimiting the driving functions to the Nyquist wavenumber.
 This can be performed by either spatially filtering the driving functions with an appropriate spatial low-pass filter prior to numerical evaluation, or performing bandlimitation directly in the wavenumber (modal) domain analytically.
@@
 \subsection{Spatial to temporal filter transform}
-First, a general transformation is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
+First, a general analytical approach is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
+From herein, subscript $x$ and $t$ distinguishes wether a filter is defined as a spatial or the temporal filters, respectively.
 
@@
 \begin{equation}
-    d'_x(s,t+ \tau(s) ) = h_x(s-s_i) \, A^D(s_i)
+    d'_x(s,t+ \tau(s) ) =  \frac{ c }{|\hat{k}_t^P(s_i)|} \, h_x(s-s_i) \, A^D(s_i)
     .
@@
 \begin{equation}
-    \tau(\vx) = \hat{k}^P_x(\vx)x +  \hat{k}^P_y(\vx) y
+    \tau(\vx) = \hat{k}^P_x(\vx) \, x +  \hat{k}^P_y(\vx) \, y
 \end{equation}
@@
 The validity and the error analysis of the above filter transform was investigated in details in \cite{Firtha DAGA2023}.
-In the following the direct application for Local WFS is discussed.
+In the following the direct application for local WFS is discussed.
 
@@
 
-From Figure \ref{Fig:aliasing} (d) it is obvious, that the overlapping of the sampled driving function spectra, and, therefore, the presence of aliasing waves can be avoided by spatially bandlimiting the driving functions to the Nyquist wavenumber prior to sampling.
-Spatial bandlimitation can be easily performed by designing a suitable spatial antialiasing filter and transforming it into an equivalent temporal filter bank, based on the results of the previous section.
+Figure \ref{Fig:aliasing} (d) reflects that the overlapping of the sampled driving function spectra, and, therefore, the presence of aliasing waves can be avoided by spatially bandlimiting the driving functions to the Nyquist wavenumber prior to sampling.
+Spatial bandlimitation can be straightforwardly performed by designing a suitable spatial antialiasing filter and transforming it into an equivalent temporal filter bank, based on the results of the previous section.
 An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensures analytical spatial bandlimitation.
@@
 \subsubsection{Symmetrical antialiasing}
-As the simplest antialiasing strategy, the spectral overlapping is avoided by the spatial lowpass filtering of the driving functions to the Nyquist wavenumber, $k_{s,\mathrm{Nyq}} = \frac{\pi}{\Delta s}$.
+As the most straightforward antialiasing strategy, the spectral overlapping is avoided by the spatial lowpass filtering of the driving functions to the Nyquist wavenumber, $k_{s,\mathrm{Nyq}} = \frac{\pi}{\Delta s}$.
 
@@
 \end{equation}
-Therefore, the cut-off frequency of the equivalent low-pass filter on a given SSD element is directly determined by the tangential component of the local propagation vector.
+Therefore, the cut-off frequency of the equivalent low-pass filter on a given SSD element is inversely proportional to the tangential component of the local propagation vector.
 
 The result of antialiasing filtering is depicted in Figure \ref{Fig:symm_antialiasing} for the synthesis scenario discussed in the foregoing.
-In the present case the sampling arc length is given by $\Delta s = \frac{2 \pi R_0}{N}$, i.e. the space-dependent cut-off frequency reads as\begin{equation}
+In the present case the sampling arc length is given by $\Delta s = \frac{2 \pi R_0}{N}$, i.e. the space-dependent cut-off frequency reads as 
+\begin{equation}
     \omega_c(s) = \frac{ N}{ 2 R_0 } \frac{c}{\hat{k}_t^P(s)}.
@@
     \begin{center}
-        \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis.png}
+        \begin{overpic}[width = 0.75\columnwidth]{figs/firtha_center.png}
             \footnotesize \put(0,2){(a)}
@@
     \end{center}
-    \caption{Symmetric antialiasing filtering}
+    \caption{Symmetric antialiasing filtering. Figure (a) depicts the synthesized wave front, and (b) illustrates the spatial spectrum of the driving functions.}
     \label{Fig:symm_antialiasing}
 \end{figure}
-It is highlighted, that the presented antialiasing strategy ensures highly suppressed aliasing waves in the center of the circular source array.
+It is highlighted that the presented antialiasing strategy ensures suppressed aliasing waves in the center of the circular source array.
 In other positions of the listening area lateral aliasing wavefronts remain in the reproduced wave field, while the target, virtual wave front is bandlimited.
@@
 
-From \eqref{eq:cutoff_fr} it is clear that since the antialiasing filter cutoff frequency is proportional to the tangential component of the virtual field on the SSD, therefore, in a circualr array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
+Since the cutoff frequency of the antialiasing filter (Eq.
+\eqref{eq:cutoff_fr} ) is inversely proportional to the tangential component of the virtual field on the SSD, therefore, in a circular array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
 This fullband SSD element is marked with white dot in Figure \ref{Fig:symm_antialiasing} (a).
@@
 The direction of the line of aliasing-free synthesis is marked with a dashed arrow in the figure.
-This is in contrast with conventional Local WFS approaches, in which the synthesis is optimized in the proximity of a pre-defined reference position over a circular area.
+This is in contrast with previous local WFS approaches, in which the synthesis is optimized in the proximity of a pre-defined reference position over a circular area.
 
@@
 \end{equation}
-Note, that in this case even the spatial filters are frequency dependent.
-This seemingly pointless assumption ensures later that the transformed temporal filters remain time-invariant.
+Note, that in this case even the spatial filters are frequency dependent, in order to ensure that the transformed temporal filters remain time-invariant, as explained in the followings.
 
@@
     \begin{center}
-        \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_steered.png}
+        \begin{overpic}[width = 0.75\columnwidth]{figs/firtha_left.png}
             \footnotesize \put(0,2){(a)}
@@
     \end{center}
-    \caption{Non-symmetric antialiasing filtering}
+    \caption{Non-symmetric antialiasing filtering. Figure (a) depicts the synthesized wave front, and (b) illustrates the spatial spectrum of the driving functions.}
     \label{Fig:assymm_antialiasing}

### 2023-06-29 paper/main.tex
matlab_added

@@
     \IEEEauthorblockN{Nara Hahn}
-    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-        \textit{name of organization (of Aff.)}\\
-        City, Country \\
-        email address or ORCID}
+    \IEEEauthorblockA{\textit{Institute of Sound and Vibration Research} \\
+        \textit{University of Southampton}\\
+        Southampton, United Kingdom \\
+        nara.hahn@soton.ac.uk}
     \and
@@
 In practical applications the SSD constist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
-This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, heavily degrading the quality of reproduction.
+This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, heavily degrading the quality of reproduction \cite{8371275, 8611109}.
 
@@
 These anti-aliased WFS approaches are commonly referred to as Local Wave Field Synthesis (LWFS).
-Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{}.
+Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{Winter2016-TASL, Hahn17:EUSIPCO}.
 However, due to the high computational demand the real-time application of these LWFS approaches is not straightforward.
@@
 The present contribution introduces a novel LWFS approach, relying merely on the temporal bandlimitation of the SSD driving functions.
-The temporal filters, defined uniquely for each SSD elements, are obtained from spatial antialiasing filters by means of an analytical spatial-to-temporal filter transformation, introduced by the current authors in a previous contribution \cite{firtha_daga}.
+The temporal filters, defined uniquely for each SSD elements, are obtained from spatial antialiasing filters by means of an analytical spatial-to-temporal filter transformation, introduced by the current authors in a previous contribution \cite{firtha_daga2023}.
 Similarly to other LWFS techniques, the presented approach ensures aliasing-free synthesis at a predefined listening position at the cost of temporally bandlimited sound field at other listening regions.
@@
 
-It should be noted that the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach:
+It should be noted that in the angular frequency domain the filtered driving function is written as
+\begin{equation}
+    D'_t(s,\omega) = D(s,\omega) H_t(s,\omega) =  H_x\left(-k_t^P(s)\right) \, D(s,\omega),
+\end{equation}
+from which formulation it is apparent that in the frequency domain the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach, and the frequency dependent spatial window is given by $H_x\left(-k_t^P(s)\right)$:
 in the aspect of antialiasing filtering SSD positions where the local wavenumber vector is higher than the Nyquist wavenumber are highly attenuated, with the window width decreasing with increasing angular frequency.

### 2023-06-29 MATLAB/spectrum_illustration.m

@@ -1,0 +1,121 @@
+clear
+close all
+
+q = 10;
+R0 = 2;
+Nssd = 4*600;
+[x0,y0] = pol2cart(linspace(0,360*(1-1/Nssd), Nssd)'*pi/180,repmat(R0,Nssd,1));
+x0 = [x0,y0];
+n0 = -x0/R0;
+
+fs = 20e3;
+N = 1024;
+xr = [0,0];
+xs = [3,0];
+omega = 2*pi*(0:N-1)'/N*fs;
+H_pre = fft(get_wfs_prefilter(N,fs),N);
+
+W = 1;
+k0a = 2;
+[amp,delay] = get_delay_and_gain(x0,n0,xs,xr);
+[AA0,k0] = get_antialiasing_filters(x0(1:q:end,:),n0(1:q:end,:),xs,xr,fs,N,W);
+AA = zeros(N,Nssd);
+AA(:,1:q:end) = AA0;
+%D_wfs = ifft((H_pre*amp.').*exp(-1i*omega*delay'),length(omega),1,'symmetric');
+D_wfs = ifft(AA.*(H_pre*amp.').*exp(-1i*omega*delay'),length(omega),1,'symmetric');
+comb = zeros(size(D_wfs));
+comb(:,1:q:end) = 1;
+D_wfs = D_wfs.*comb;
+
+
+ks = ((0:Nssd-1)-Nssd/2)/Nssd*q;
+Dks = fft2(D_wfs,size(D_wfs,1),size(D_wfs,2));
+
+ftsize = 12;
+f = figure('units','normalized','outerposition',[0.2 0.3 0.35 0.4]);
+set(f,'defaulttextinterpreter','latex')
+
+pos =  [0.11,0.19,0.85,0.75];
+p1 = axes('Units','normalized','Position',pos(1,:));
+
+x = ks;
+y =  omega/2/pi/fs;
+pcolor( x,y, q*abs(fftshift(Dks,2)));
+yl0 = [0,0.5];
+ylim(yl0)
+xlim([-1,1])
+caxis([0,50])
+shading interp
+
+hold on
+% plot([0,-k0],yl0,'-w','LineWidth',1)
+% plot([-0.5/W,-0.5/W-k0],yl0,'--w','LineWidth',1)
+% plot([0+0.5/W,0+0.5/W-k0],yl0,'--w','LineWidth',1)
[…]

### 2023-06-29 MATLAB/spectrum_illustration.m
matlab_added

@@ -15,10 +15,10 @@ xs = [3,0];
 omega = 2*pi*(0:N-1)'/N*fs;
 H_pre = fft(get_wfs_prefilter(N,fs),N);
 
-W = 1;
+W0 = 1;
 k0a = 2;
 [amp,delay] = get_delay_and_gain(x0,n0,xs,xr);
-[AA0,k0] = get_antialiasing_filters(x0(1:q:end,:),n0(1:q:end,:),xs,xr,fs,N,W);
+[AA0,k0] = get_antialiasing_filters(x0(1:q:end,:),n0(1:q:end,:),xs,xr,fs,N,W0);
 AA = zeros(N,Nssd);
 AA(:,1:q:end) = AA0;
 %D_wfs = ifft((H_pre*amp.').*exp(-1i*omega*delay'),length(omega),1,'symmetric');

### 2023-06-29 paper/main.tex
matlab_added

@@
 \section{Comparison with direct modal bandlimitation}
-Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.
-
-\input{lwfs-spl.tex}
-
 \begin{figure*}[h!]
     \begin{center}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center.png}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center2.png}
             \footnotesize \put(0,2){(a)}
+            \footnotesize \put(45,102){Center}
         \end{overpic} \hspace{3mm}
-        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_right.png}
+        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_left2.png}
             \footnotesize \put(0,2){(b)}
+            \footnotesize \put(45,102){Left}
         \end{overpic}\hspace{3mm}
@@
             \footnotesize \put(0,2){(c)}
+            \footnotesize \put(45,102){Front}
         \end{overpic} \hspace{3mm}
@@
             \footnotesize \put(0,2){(d)}
+            \footnotesize \put(45,102){Back}
         \end{overpic}\\  \vspace{5mm}
@@
     \end{center}
-    \caption{fg}
+    \caption{Comparison of the proposed, temporal filtering/based LWFS approach with direct modal bandlimitation.
+    }
     \label{Fig:aliasing}
 \end{figure*}
+
+Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.
+
+\input{lwfs-spl.tex}
 

### 2023-06-29 MATLAB/spectrum_illustration.m

@@ -3,7 +3,7 @@ close all
 
 q = 10;
 R0 = 2;
-Nssd = 4*600;
+Nssd = 2400;
 [x0,y0] = pol2cart(linspace(0,360*(1-1/Nssd), Nssd)'*pi/180,repmat(R0,Nssd,1));
 x0 = [x0,y0];
 n0 = -x0/R0;

### 2023-06-29 paper/main.tex
matlab_added

@@
 These anti-aliased WFS approaches are commonly referred to as Local Wave Field Synthesis (LWFS).
-Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{Winter2016-TASL, Hahn17:EUSIPCO}.
+Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{Winter2016-TASL, Hahn16:AES, Hahn17:EUSIPCO, hahn2022cylindrical}.
 However, due to the high computational demand the real-time application of these LWFS approaches is not straightforward.
@@
 This can be performed by either spatially filtering the driving functions with an appropriate spatial low-pass filter prior to numerical evaluation, or performing bandlimitation directly in the wavenumber (modal) domain analytically.
-The latter approach is implemented by \cite{Nara and Fiete}, and will serve as a reference solution in the following investigation.
+The latter approach is implemented by \cite{hahn2022cylindrical}, and will serve as a reference solution in the following investigation.
 However, the modal bandlimitation solution is available only for plane wave and point source virtual source models synthesized by a circular SSD, at the cost of increased computational complexity.
@@
     \caption{Comparison of the proposed, temporal filtering/based LWFS approach with direct modal bandlimitation.
-    }
-    \label{Fig:aliasing}
+    First row (a-d) depicts the synthesized field with temporal LWFS, Second row (e-h) depicts the synthesized field with modal bandlimitation and third row (i-l) compares the frequency response at the reference position.}
+    \label{Fig:comparison}
 \end{figure*}
@@
 Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.
+\input{lwfs-spl.tex}
 
-\input{lwfs-spl.tex}
+The two methods are compared via the exemplary synthesis scenario discussed in the foregoing, synthesizing an impulsive plane wave.
+The result of synthesis for four different reference positions are investigated:
+\begin{itemize}
+    \item Center: $\vxref = \left[0,0,0\right]^{\mathrm{T}}$
+    \item Left: $\vxref = \left[0,1,0\right]^{\mathrm{T}}$
+    \item Back: $\vxref = \left[-1,0,0\right]^{\mathrm{T}}$
+    \item Front: $\vxref = \left[1,0,0\right]^{\mathrm{T}}$
+\end{itemize}
+Figure \ref{Fig:comparison} presents the comparison of the result of the two approaches, each column illustrating a different reference position.
+The first row (a-d) shows the synthesized field at the time instant of the plane wave pass-by through the reference position by implementing the proposed LWFS approach, with the second row (e-h) depicting the same result with using modal bandlimitation.
+The third row illustrates the measured frequency response of the synthesized fields at the reference positions.
 

### 2023-06-29 paper/main.tex
..

@@
 \begin{equation}
-    \tau(\vx) = \hat{k}^P_x(\vx) \, x +  \hat{k}^P_y(\vx) \, y
+   \tau(\vx) = \frac{\hat{k}^P_x(\vx) \, x +  \hat{k}^P_y(\vx) \, y}{c}
 \end{equation}
@@
 Spatial bandlimitation can be straightforwardly performed by designing a suitable spatial antialiasing filter and transforming it into an equivalent temporal filter bank, based on the results of the previous section.
-An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensures analytical spatial bandlimitation.
+An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensures analytical spatial bandlimitation\footnote{
+    The above statement holds as long as temporally continuous driving functions are assumed.
+Once the driving functions are sampled with a sampling frequency $f_s = 1 /\Delta t$, this corresponds to a spatial sampling prior to the filtering process with $\Delta s = c/f_s$.}.
 
@@
     \end{center}
-    \caption{Comparison of the proposed, temporal filtering/based LWFS approach with direct modal bandlimitation.
+    \caption{Comparison of the proposed, temporal filtering-based LWFS approach with direct modal bandlimitation.
     First row (a-d) depicts the synthesized field with temporal LWFS, Second row (e-h) depicts the synthesized field with modal bandlimitation and third row (i-l) compares the frequency response at the reference position.}
@@
 
-The two methods are compared via the exemplary synthesis scenario discussed in the foregoing, synthesizing an impulsive plane wave.
-The result of synthesis for four different reference positions are investigated:
+The two methods are compared via the exemplary synthesis scenario discussed in the foregoing, synthesizing an impulsive plane wave, by bandlimiting the driving functions to the Nyquist wavenumber.
+The result of synthesis is investigated for four different reference positions:
 \begin{itemize}
@@
 
+The figures reflects that both methods are capable of sufficient suppression of the aliasing wave fronts at the prescribed reference position in a qualitatively similar manner.
+The measured frequency responses show that the presented approach slightly suffers from ripples above the spatial aliasing frequency.
+This remaining aliasing artifact can be explained as the result of the approximations, introduced in the derivation of the temporal-to-spatial filter transform.
+
+In the center position the modal bandlimitation approach serves as a reference solution, with nearly perfect aliasing suppression.
+For off-center positions both methods suffers from remaining aliasing artifacts.
+This effect is even enhanced in the case of the front position, in which case the receiver/reference position is closer to the stationary SSD position (white SSD element).
+The phenomena is explained by the spatial variation of the spatial aliasing frequency and the aliasing intensity, which has been already investigated in details in \cite{8611109} in a geometrical manner.
+The incorporation of this effect in the present antialiasing strategy is the subject of a further research. 
+Yet, it has been already reported that choosing a non-critical modal bandwidth below the Nyquist wavenumber is an efficient strategy to avoid these remaining aliasing wavefront \cite{Hahn17:EUSIPCO}.
+
 \section{Conclusion}
+
+The present contribution discussed a novel local Wave Field Synthesis approach, relying on a suitable filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
+By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals, with the bandlimit depending on the virtual source model.
 

### 2023-06-29 paper/main.tex
..

@@
 This formulation applies to both plane waves and (3D) point sources.
-The propagation dynamics of the sound field are governed by its phase function $\tau(\vx)$, termed as the eikonal in the field of ray acoustics.
+The propagation dynamics of the sound field are governed by its phase function $\tau(\vx)$, termed as the eikonal in the field of ray acoustics \cite{Bleistein2000}.
 In the temporal domain, the sound field can be obtained by taking the inverse Fourier transform of \eqref{eq:Pxw}, yielding:

### 2023-06-29 paper/main.tex
..

@@
 \end{multline}
-In order to evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd}, which states that
+In order to evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd, Jackson1999}, which states that
 \begin{equation}
@@
 The present contribution discussed a novel local Wave Field Synthesis approach, relying on a suitable filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
-By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals, with the bandlimit depending on the virtual source model.
+By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals.
+With the above antialiasing strategy local WFS can be implemented by choosing an appropriate spatial antialiasing filter based on a predefined reference listening position.
 

### 2023-06-29 paper/main.tex
spectra_added

@@
 \section{Comparison with direct modal bandlimitation}
-\begin{figure*}[h!]
+
+\begin{figure}[]
+    \begin{center}
+        \begin{overpic}[width = 0.75\columnwidth]{figs/nara_spectrum_center.png}
+            \footnotesize \put(0,2){(a)}
+        \end{overpic}
+        \\
+        \begin{overpic}[width = 0.75\columnwidth]{figs/nara_spectrum_left.png}
+            \footnotesize \put(0,0){(b)}
+        \end{overpic}
+    \end{center}
+    \caption{Spectrum of LWFS driving functions by direct modal bandlimitation with the reference position choosen at the center, $\vxref = \left[0,0,0\right]^{\mathrm{T}}$ (a) and on the left side, $\vxref = \left[0,1,0\right]^{\mathrm{T}}$ (b).
+    }
+    \label{Fig:nara_spectrum}
+\end{figure}
+
+\begin{figure*}[]
     \begin{center}
@@
 \end{itemize}
-Figure \ref{Fig:comparison} presents the comparison of the result of the two approaches, each column illustrating a different reference position.
+
+For the central and the left reference positions first the spectra of the driving functions were investigated.
+Figure \ref{Fig:nara_spectrum} already reflects the fact that the proposed temporal LWFS approach is an approximation of the reference solution, i.e. of the direct modal bandlimitation.
+It is verified that modal bandlimitation LWFS performs the same "steering" of the modal spectrum into the direction of the central wavenumber, realizing a freuqency dependent spatial band-pass filter.
+
+Figure \ref{Fig:comparison} presents the comparison of the result of the two approaches via the synthesized field and the frequency response, each column illustrating a different reference position.
 The first row (a-d) shows the synthesized field at the time instant of the plane wave pass-by through the reference position by implementing the proposed LWFS approach, with the second row (e-h) depicting the same result with using modal bandlimitation.
@@
 
-The present contribution discussed a novel local Wave Field Synthesis approach, relying on a suitable filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
+The present contribution discussed a novel local Wave Field Synthesis approach, relying on a filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
 By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals.
 With the above antialiasing strategy local WFS can be implemented by choosing an appropriate spatial antialiasing filter based on a predefined reference listening position.
+
+It was demonstrated via numerical simulations that the approach is capable of the suppression of aliasing wavefronts along a straight line/ray (containing the reference position) with its direction of adjusted by the center wavenumber of the antialiasing spatial band-pass filter.
+The performance of the presetned approach was compared with LWFS by direct modal bandlimitation as a direct, reference solution.
+It was shown, that temporal LWFS gives a feasible approximation for the reference, while being a more robust approach, with less computational demand, allowing real-time implementations.
 

### 2023-06-29 paper/main.tex
spectra_added

@@
 
-The present contribution discussed a novel local Wave Field Synthesis approach, relying on a filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
-By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals.
-With the above antialiasing strategy local WFS can be implemented by choosing an appropriate spatial antialiasing filter based on a predefined reference listening position.
+The present contribution discussed a novel local Wave Field Synthesis approach, allowing an increased synthesis accuracy in the proximity of a reference position when a sparse SSD is applied for sound field reproduction.
+The approach relies on a filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
+Local WFS is achieved by spatial bandlimiting of the SSD driving function to the Nyquist wavenumber, achieved by suitable spatial filtering.
+By transforming the spatial antialiasing filters to a temporal filter bank, LWFS can be performed by the simple temporal bandlimitation of the SSD driving signals.
 
-It was demonstrated via numerical simulations that the approach is capable of the suppression of aliasing wavefronts along a straight line/ray (containing the reference position) with its direction of adjusted by the center wavenumber of the antialiasing spatial band-pass filter.
-The performance of the presetned approach was compared with LWFS by direct modal bandlimitation as a direct, reference solution.
-It was shown, that temporal LWFS gives a feasible approximation for the reference, while being a more robust approach, with less computational demand, allowing real-time implementations.
+It was demonstrated via numerical simulations that the approach is capable of the suppression of aliasing wavefronts along a straight line/ray, passing through a predefined the reference position.
+The direction of antialiasing synthesis can be set by adjusting the center wavenumber of the antialiasing spatial band-pass filter.
+The performance of the presetned approach was compared with LWFS by direct modal bandlimitation taken as a direct, reference solution.
+It was shown that temporal LWFS gives a feasible approximation for the reference one, while being a more robust approach with less computational demand, allowing even real-time implementations. 
+Furthermore, altough the proposed approach was validated via the example of a virtual plane wave, the technique is capable of the aliasing-free synthesis of an arbitrary simple virtual field model.
+
+It was demonstrated that both approaches suffer for remaining aliasing artifacts in off-center reference positions that's suppression is the topic of further research.
+
+Finally, as an important limitation of the proposed technique it has to be pointed out, that since the proposed approach bandlimits the driving signals as the function of the local propagation direction of the virtual field on the SSD, therefore, the overall synthesis bandlimit varies with the virtual source direction/position.
+This can result in enhanced artifacts in case of a non-stationary virtual field, e.g. in case of the synthesis of a moving source.
+The workaround for this phenomena is also the subject of future research.
 

### 2023-06-29 paper/main.tex
fs_revision_started

@@
 \section{Introduction}
+\label{sec:introduction}
 The aim of sound field synthesis is to reproduce a virtual target sound field over an extended listening area using a densely spaced loudspeaker arrangement, known as the secondary source distribution (SSD).
@@
 As WFS obtains the necessary driving functions from a suitable boundary integral representation of the target sound field, perfect phase correct field-reconstruction could be only achieved by employing a theoretical, continuous secondary source distribution.
-In practical applications the SSD constist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
-This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, heavily degrading the quality of reproduction \cite{8371275, 8611109}.
+In practical applications the SSD consist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
+This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, degrading the quality of reproduction \cite{8371275, 8611109}.
 
-The effect of aliasing can be mitigated by restricting the synthesis to a smaller control region inside the listening area at the cost of permitting stronger aliasing artifacts outside the control region.
+The effect of aliasing can be mitigated by restricting the synthesis to a smaller control region inside the listening area at the cost of permitting stronger aliasing artifacts outside the region of interest.
 These anti-aliased WFS approaches are commonly referred to as Local Wave Field Synthesis (LWFS).
-Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{Winter2016-TASL, Hahn16:AES, Hahn17:EUSIPCO, hahn2022cylindrical}.
+Recently introduced LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{Winter2016-TASL, Hahn16:AES, Hahn17:EUSIPCO, hahn2022cylindrical}.
 However, due to the high computational demand the real-time application of these LWFS approaches is not straightforward.
@@
 Similarly to other LWFS techniques, the presented approach ensures aliasing-free synthesis at a predefined listening position at the cost of temporally bandlimited sound field at other listening regions.
-The results of the proposed approach are compared with a conventional LWFS approach employing direct spatial bandlimitation.
+The results of the proposed approach are compared with a recent LWFS approach employing direct spatial bandlimitation.
+
+The paper is organized as follows:
+Section \ref{sec:theory} gives a brief theoretical introduction on basic WFS theory and spatial aliasing phenomena. 
+Section \ref{sec:novel_approach} first discusses the spatial-to-temporal filter transform, then introduces the novel local WFS methodology.
+Section \ref{sec:evaluation} gives a comparison of the presented technique with a recent LWFS approach based on direct modal bandlimitation, followed by a short summary and outlook in section \ref{sec:conclusion}.
 
 \section{Theoretical basics}
+\label{sec:theory}
+
 \subsection{The local propagation vector:}
 Consider an arbitrary steady-state free space sound field at an angular frequency $\omega$.
-As a standard ansatz in the field of geometrical acoustics the sound field can be written in the general polar from as
+As a standard ansatz in the field of geometrical acoustics the sound field is written in the general polar from as
 %
@@
 \subsection{Conventional 2.5D Wave Field Synthesis}
-Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D freefield Green's function.
+Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D freefield Green's function, reading in the frequency domain as
+\begin{equation}
+    G_{3 \mathrm{D}}(\vx,\vxo,\omega) = \frac{1}{4\pi}\frac{\te^{-\frac{\omega}{c}\left| \vx-\vxo\right|}}{\left| \vx-\vxo\right|},
+\end{equation}
+where $\omega$ denotes the angular frequency.
 In this geometry the target field inside the area bounded by the SSD is described by the  Kirchhoff approximation of 2.5D Kirchhoff-Helmholtz integral, from which the 2.5D driving functions can be extracted.
@@
 \begin{itemize}
-    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$,
-    \item a secondary source selection window
+    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$ \cite{Start1997:phd, doi:10.1121/1.404755, Bleistein1986},
+    \item a secondary source selection window \cite{Nicol1999, Spors2007}
           \begin{equation}
@@
           where $\hat{k}_{\mathrm{n}}^P(\vxo)$ is the normal component of the local propagation vector,
-    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (c.f. \cite{Firtha2016}),
+    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (c.f.
+\cite{Start1997:phd} and for a more complete treatise \cite{Firtha2016}),
     \item and the virtual field measured on the SSD.
@@
 with $A^D(\vxo)$ being the real valued overall gain factor of the driving function, $\ast_t$ denoting temporal convolution and $h_{\text{pre}}(t)$ is the temporal WFS prefilter impulse response.
-The analytical pre-equalization filter impulse response is given in \cite{Deregowski1983, Firtha2019phd}, while for an ideal FIR filter implementation the reader is referred to \cite{Schultz2016}.
+The analytical, continuous pre-equalization filter impulse response is given in \cite{Deregowski1983, Firtha2019phd}, while for an ideal, non-casual FIR filter implementation the reader is referred to \cite{Schultz2016}.
 In the following due to the associativity of convolution this prefiltering is excluded from the discussion.
@@
     \end{center}
-    \caption{The synthesized field and the spatial spectrum of the driving function in case of ideal, quasi-continuous SSD (a) and (c), and in case of a discretized SSD (b) and (d).
-    It is important ot note that the spatial spectrum depicts only the non-zero Fourier components (i.e. the Fourier series coefficients) normalized to the sampling wavenumber.}
+    \caption{The synthesized field (top) and the spatial spectrum (bottom) of the driving function in case of ideal, quasi-continuous SSD (a) and (c), and in case of a discretized SSD (b) and (d).
+    It is important to note that the spatial spectrum depicts only the non-zero Fourier components (i.e. the Fourier series coefficients) normalized to the sampling wavenumber.}
     \label{Fig:aliasing}
 \end{figure*}
-Conventional WFS theory assumes a continuous secondary source distribution.
+The backbone of WFS theory assumes a continuous secondary source distribution.
 In practical applications the SSD is composed of evenly spaced discrete source elements.
@@
 the arc length $s = R_0\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
-The discretization process is given by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas in the actual secondary source positions:
+The discretization process is modeled by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas, where the impulse occurences match the actual SSD positions:
 \begin{equation}
@@
 \end{equation}
-where $t \rightarrow \omega$ and $s \rightarrow k_s$ are Fourier-transform pairs.
-Obviously, for a closed SSD contour (most notablz for a circular SSD) the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial wavenumber, i.e.
+where $t \rightarrow \omega$ and $s \rightarrow k_s$ are variables pairs for the Fourier-transform.
+Obviously, for a closed SSD contour (most notably for a circular SSD) the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial wavenumber, i.e.
 at
@@
 
-In the followings the spatial spectrum refers to the distribution of the non-zero wavenumber values, and the corresponding wavenumber refers to the spatial frequency of the harmonic basis functions, measured along the closed curve.
+In the followings the spatial spectrum refers to the distribution of the non-zero wavenumber values, and the corresponding wavenumber refers to the spatial frequency (multipled by $2\pi$) of the harmonic basis functions, measured along the closed curve.
 Figure \ref{Fig:aliasing} (c) and (d) illustrate the quasi-continuous and the sampled driving function's spectra.
 
-From \eqref{eq:sampling_fd} it can be concluded that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber $k_{s, \mathrm{s}} = \frac{2\pi}{\Delta s}$.
-Since the conventional driving functions are not-bandlimited, therefore, the repeating spectra will overlap above the Nyquist wavenumber $k_{s, \mathrm{Nyq}} = \frac{\pi}{\Delta s}$, for which the corresponding angular frequency is the aliasing frequency of the discretization scheme, as depicted in \ref{Fig:aliasing} (d).
+From \eqref{eq:sampling_fd} it can be concluded that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber
+\begin{equation}
+k_{s, \mathrm{s}} = \frac{2\pi}{\Delta s}.
+\end{equation}
+Since the conventional driving functions are not-bandlimited, therefore, the repeating spectra will overlap above the Nyquist wavenumber $k_{s, \mathrm{Nyq}} = \frac{\pi}{\Delta s}$, for which the corresponding angular frequency is the aliasing frequency of the discretization scheme, as depicted in Figure \ref{Fig:aliasing} (d).
 
@@
 
-\section{Time domain antialiasing filter}
+\section{Time domain antialiasing LWFS}
+\label{sec:novel_approach}
 
@@
 First, a general analytical approach is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
-From herein, subscript $x$ and $t$ distinguishes wether a filter is defined as a spatial or the temporal filters, respectively.
+From herein, subscript $x$ and $t$ distinguishes wether a filter is defined as a spatial or a temporal filter, respectively.
 
@@
 The following transformation is allowed by the spatio-temporal structures of the conventional driving functions \eqref{eq:d_wfs_td}, in which the spatial and temporal dimensions are interconnected in the argument of a Dirac-delta, due to the wave propagation characteristics.
-The main idea of the derivation is that by exploiting the sifting property of the Dirac-delta in the driving functions, both spatial and temporal convolutions \eqref{eq:spatial_conv} and \eqref{eq:temp_conv} can be evaluated, from which the temporal filter impulse responses can be expressed as the function of the spatial one.
+The main idea of the derivation is that by exploiting the sifting property of the Dirac-delta in the driving functions, both spatial and temporal convolutions \eqref{eq:spatial_conv} and \eqref{eq:temp_conv} can be evaluated, from which the temporal filter impulse responses can be expressed as the function of the spatial ones.
 Again, in the following the pre-equalization filter is omitted from discussion, since equalization filtering can be performed following the antialiasing process.
@@
 \section{Comparison with direct modal bandlimitation}
+\label{sec:evaluation}
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
 

### 2023-06-30 paper/main.tex
corrections

@@
 \begin{itemize}
-    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$ \cite{Start1997:phd, doi:10.1121/1.404755, Bleistein1986},
+    \item a frequency dependent pre-equalization filter $H_{\text{pre}}(\omega)$ \cite{Start1997:phd, Berkhout1993:Acoustic_control_by_WFS, Bleistein1986},
     \item a secondary source selection window \cite{Nicol1999, Spors2007}
@@
 \end{equation}
-where $k_t^P(s)$ is the tangential component of the local wavenumber vector, being a vector in a steady state sound field, pointing in the local propagation direction with the length being $\omega/c$ \cite{Firtha2019phd}.
+where $k_t^P(s)$ is the tangential component of the local wavenumber vector \footnote{The local wavenumber vector can be defined for a steady state sound field, pointing in the local propagation direction with the length being $\omega/c$ \cite{Firtha2019phd}}.
 Hence, as the main result of the present discussion, the temporal filter transfer can be obtained from the wavenumber (modal) content of the spatial filter by simple rescaling in terms of the local wavenumber vector.
 
-The validity and the error analysis of the above filter transform was investigated in details in \cite{Firtha DAGA2023}.
+The validity and the error analysis of the above filter transform was investigated in details in \cite{firtha_daga2023}.
 In the following the direct application for local WFS is discussed.
@@
 Spatial bandlimitation can be straightforwardly performed by designing a suitable spatial antialiasing filter and transforming it into an equivalent temporal filter bank, based on the results of the previous section.
-An important advantage of the above temporal filtering is that the driving functions may be evaluated in the discrete SSD positions, and a subsequent temporal antialiasing inherently ensures analytical spatial bandlimitation\footnote{
+An important advantage of the temporal filtering approach instead of direct spatial filtering is that analyical spatial bandlimitation can be achieved by calculating the WFS driving functions at discrete positions, followed by temporal filtering \footnote{
 The above statement holds as long as temporally continuous driving functions are assumed.
@@
 \end{equation}
-The antialiasing filters were a 4-th order Butterworth deisgn.
+The antialiasing filters are 4-th order Butterworth designs.
 
@@
 In other positions of the listening area lateral aliasing wavefronts remain in the reproduced wave field, while the target, virtual wave front is bandlimited.
-This phenomena can be easily understood by investigating the synthesis scenario in a geometrical manner:
+This phenomenon can be easily understood by investigating the synthesis scenario in a geometrical manner:
 
 Since the cutoff frequency of the antialiasing filter (Eq.
-\eqref{eq:cutoff_fr} ) is inversely proportional to the tangential component of the virtual field on the SSD, therefore, in a circular array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
+\eqref{eq:cutoff_fr}) is inversely proportional to the tangential component of the virtual field on the SSD, therefore, in a circular array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly (i.e.
+where the tangential component of the local propagation vector is zero).
 This fullband SSD element is marked with white dot in Figure \ref{Fig:symm_antialiasing} (a).
@@
 
-It should be noted that in the angular frequency domain the filtered driving function is written as
+It should be noted that in the angular, temporal frequency domain the filtered driving function is written as
 \begin{equation}

### 2023-06-30 paper/lwfs-spl.tex
matlab_added
corrections_applied

@@
-\ldots
 For a direct spatial band-limitation,
@@
 ranging between 273 and 787 taps for the considered scenarios
-(excluding the WFS pre-filter).
+(excluding the WFS prefilter).
 %

### 2023-06-30 paper/main.tex
corrections_applied

@@
 \usepackage{xcolor}
+\usepackage{nicefrac}
 \usepackage{overpic,subfigure, tikz}
@@
 
-\title{Local Wave Field Synthesis by Temporal Bandlimitation*
+\title{Local Wave Field Synthesis by Temporal Bandlimitation
     \thanks{This work was supported by the János Bolyai Research Scholarship of the Hungarian Academy of Sciences, the ÚNKP-22-5-BME-318 New National Excellence Program of the Ministry for Innovation and Technology from the source of the National Research, Development and Innovation Fund
@@
 In practical applications the SSD consist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
-This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, degrading the quality of reproduction \cite{8371275, 8611109}.
+This spatial aliasing phenomenon is perceived as coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, degrading the quality of reproduction \cite{8371275, 8611109}.
 
@@
 Section \ref{sec:novel_approach} first discusses the spatial-to-temporal filter transform, then introduces the novel local WFS methodology.
-Section \ref{sec:evaluation} gives a comparison of the presented technique with a recent LWFS approach based on direct modal bandlimitation, followed by a short summary and outlook in section \ref{sec:conclusion}.
+Section \ref{sec:evaluation} gives a comparison of the presented technique with a recent LWFS approach based on direct modal bandlimitation, followed by a short summary and outlook in Section \ref{sec:conclusion}.
 
@@
 
-\subsection{The local propagation vector:}
+\subsection{Local propagation vector concept}
 Consider an arbitrary steady-state free space sound field at an angular frequency $\omega$.
-As a standard ansatz in the field of geometrical acoustics the sound field is written in the general polar from as
+As a standard ansatz in the field of geometrical acoustics the sound field at a spatial position $\vx = [x\, y\, z]^{\mathrm{T}}$ is written in the general polar from as
 %
@@
 The propagation dynamics of the sound field are governed by its phase function $\tau(\vx)$, termed as the eikonal in the field of ray acoustics \cite{Bleistein2000}.
-In the temporal domain, the sound field can be obtained by taking the inverse Fourier transform of \eqref{eq:Pxw}, yielding:
+In the temporal domain, the sound field can be obtained by taking the inverse temporal Fourier-transform of \eqref{eq:Pxw}, yielding
 \begin{equation}
@@
 \end{equation}
-From the above formulation it is evident that the eikonal $\tau(\vx)$ describes the propagation delay the wavefront takes to arrive at $\vx$.
+From the above formulation it is evident that the eikonal $\tau(\vx)$ describes the propagation delay, the wavefront takes to arrive at $\vx$.
 The eikonal equation is obtained by substituting the ansatz \eqref{eq:Pxw} into the Helmholtz equation, stating that in a source free volume
@@
 is fulfilled.
-The gradient of the eikonal is termed as the local propagation vector
+The gradient of the eikonal weighted by the speed of sound is termed as the local propagation vector
 \begin{equation}
-    \hat{\vk}^P(\vx) = \posvec{3}{\hat{k}_x^P(\vx)}{\hat{k}_y^P(\vx)}{\hat{k}_z^P(\vx)} = c \nabla \tau(\vx,\omega).
+    c \nabla \tau(\vx,\omega) = \hat{\vk}^P(\vx) = \posvec{3}{\hat{k}_x^P(\vx)}{\hat{k}_y^P(\vx)}{\hat{k}_z^P(\vx)}.
 \end{equation}
@@
 
-\subsection{Conventional 2.5D Wave Field Synthesis}
+\subsection{2.5D Wave Field Synthesis}
 Consider a smooth convex secondary source distribution located at $\vxo = \posvec{3}{x_0}{y_0}{0}$ consisting of a continuous distribution of 3D point sources, described by the 3D freefield Green's function, reading in the frequency domain as
 \begin{equation}
-    G_{3 \mathrm{D}}(\vx,\vxo,\omega) = \frac{1}{4\pi}\frac{\te^{-\frac{\omega}{c}\left| \vx-\vxo\right|}}{\left| \vx-\vxo\right|},
+    G_{3 \mathrm{D}}(\vx,\vxo,\omega) = \frac{1}{4\pi}\frac{\te^{-\ti \frac{\omega}{c}\parallel \vx-\vxo \parallel }}{\parallel \vx-\vxo\parallel },
 \end{equation}
 where $\omega$ denotes the angular frequency.
-In this geometry the target field inside the area bounded by the SSD is described by the  Kirchhoff approximation of 2.5D Kirchhoff-Helmholtz integral, from which the 2.5D driving functions can be extracted.
-For an arbitrary simple target virtual sound field $P(\vxo,\omega)$ the steady-state driving functions read as \cite{Firtha2016}
+In this geometry the target field inside the area bounded by the SSD is described by the  Kirchhoff approximation of 2.5D Kirchhoff-Helmholtz integral, from which the 2.5D driving functions can be extracted \cite{Bleistein1986}.
+For an arbitrary, simple target virtual sound field $P(\vxo,\omega)$ the steady-state driving functions read as \cite{Firtha2016}
 \begin{equation}
@@
           \end{equation}
-          where $\hat{k}_{\mathrm{n}}^P(\vxo)$ is the normal component of the local propagation vector,
-    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (c.f.
-\cite{Start1997:phd} and for a more complete treatise \cite{Firtha2016}),
+          where $\hat{k}_{\mathrm{n}}^P(\vxo)$ is the normal component of the local propagation vector (i.e. its projection to the SSD normal vector at $\vxo$),
+    \item a gain factor $\sqrt{d_{\mathrm{ref}}(\vxo)}$ allowing amplitude correction along a reference curve, depending on the actual virtual field model (cf. \cite{Start1997:phd, Firtha2016}),
     \item and the virtual field measured on the SSD.
@@
 The analytical, continuous pre-equalization filter impulse response is given in \cite{Deregowski1983, Firtha2019phd}, while for an ideal, non-casual FIR filter implementation the reader is referred to \cite{Schultz2016}.
-In the following due to the associativity of convolution this prefiltering is excluded from the discussion.
+In the following due to the associativity of convolution this prefiltering is excluded from a more convenient discussion.
 
@@
     \caption{The synthesized field (top) and the spatial spectrum (bottom) of the driving function in case of ideal, quasi-continuous SSD (a) and (c), and in case of a discretized SSD (b) and (d).
-    It is important to note that the spatial spectrum depicts only the non-zero Fourier components (i.e. the Fourier series coefficients) normalized to the sampling wavenumber.}
+    It is important to note that the spatial spectrum depicts only the non-zero Fourier components (i.e. the Fourier-series coefficients) normalized to the sampling wavenumber.}
     \label{Fig:aliasing}
@@
 In practical applications the SSD is composed of evenly spaced discrete source elements.
-As a result, \emph{aliasing wavefronts} emerge from the individual secondary sources, following the intended virtual wavefront, leading to a \emph{spatial aliasing phenomena}.
-Although localization does not degrade due to the precedence effect, aliasing is perceived as strong coloration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occurring predominantly above the \emph{aliasing frequency}.
+As a result, aliasing wavefronts emerge from the individual secondary sources, following the intended virtual wavefront, leading to spatial aliasing phenomena.
+Although localization does not degrade due to the precedence effect, aliasing is perceived as strong coloration predominantly in the high-frequency region varying with the receiver position and the virtual source position/direction, occurring predominantly above the aliasing frequency.
 
 Figure \ref{Fig:aliasing} illustrates spatial aliasing in the temporal domain through the example of the synthesis of an impulsive plane wave, arriving from $\phi_{\mathrm{PW}} = 0^{\circ}$, applying a discrete secondary source distribution in comparison with a quasi-continuous synthesis scenario.
-In the current example the SSD is a circular one with the radius of $R_0 = 2~\mathrm{m}$, consisting of $N_0 = 90$ 3D point sources.
+In the current example a circular SSD is applied with the radius of $R_0 = 2~\mathrm{m}$, consisting of $N_0 = 90$ 3D point sources.
 The aliased synthesis in the temporal domain is depicted in Figure \ref{Fig:aliasing} (b).
 
-Mathematically, aliasing can be modeled as the discretization of the theoretically continuous driving functions:
+Mathematically, aliasing can be modeled as the discretization of the theoretically continuous driving functions.
 Assume that a suitable parametrization $d(s,t)$ of the secondary source is given, e.g.
-the arc length $s = R_0\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
+the arc length $s = R_0\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite, linear SSD.
 The discretization process is modeled by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas, where the impulse occurences match the actual SSD positions:
@@
 \end{equation}
-where $\Delta s$ is the sampling arc length.
+with $\Delta s$ being the sampling (arc) length.
 
@@
 \begin{equation}
-    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}\left(k_s- \nu \frac{2\pi}{\Delta s},\omega\right) \Delta s,
+    \tilde{D}_s(k_s,\omega) = \sum_{\nu = -\infty}^{\infty} \tilde{D}\left(k_s- \nu \frac{2\pi}{\Delta s},\omega\right),
     \label{eq:sampling_fd}
 \end{equation}
-where $t \rightarrow \omega$ and $s \rightarrow k_s$ are variables pairs for the Fourier-transform.
-Obviously, for a closed SSD contour (most notably for a circular SSD) the continuous spatial Fourier-transform yields a discrete spectrum, consisting of non-zero components only on the multiples of the spatial wavenumber, i.e.
+where $t \rightarrow \omega$ and $s \rightarrow k_s$ are variable pairs for the Fourier-transform.
+Obviously, for a closed SSD contour (most notably for a circular SSD) the continuous spatial Fourier-transform yields non-zero components at discrete spatial frequencies on the multiples of the spatial wavenumber, i.e.
 at
@@
 \end{equation}
-constituting a Fourier series.
+with $m \in \mathbb{Z}$ constituting a Fourier-series.
 
-In the followings the spatial spectrum refers to the distribution of the non-zero wavenumber values, and the corresponding wavenumber refers to the spatial frequency (multipled by $2\pi$) of the harmonic basis functions, measured along the closed curve.
+In the followings the spatial spectrum refers to the distribution of the non-zero wavenumber values, and the corresponding wavenumber refers to the spatial frequency (multiplied by $2\pi$) of the harmonic basis functions, measured along the closed curve.
 Figure \ref{Fig:aliasing} (c) and (d) illustrate the quasi-continuous and the sampled driving function's spectra.
 
-From \eqref{eq:sampling_fd} it can be concluded that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber
+From \eqref{eq:sampling_fd} it can be deduced that due to spatial sampling, the wavenumber content of the driving function is repeated on the multiples of the sampling wavenumber
 \begin{equation}
@@
 The latter approach is implemented by \cite{hahn2022cylindrical}, and will serve as a reference solution in the following investigation.
-However, the modal bandlimitation solution is available only for plane wave and point source virtual source models synthesized by a circular SSD, at the cost of increased computational complexity.
+However, the modal bandlimitation solution is available only for plane wave and point source virtual source models, at the cost of increased computational complexity.
 
-In the following an alternative, approximate solution is presented, allowing spatial antialiasing filtering for an arbitrary virtual source model and arbitrary SSD contour, performed by FIR filtering in the temporal domain.
+In the following an alternative, approximate solution is presented, allowing spatial antialiasing filtering for an arbitrary virtual source model and arbitrary SSD contour, performed by FIR (finite impulse response) filtering in the temporal domain.
 The technique relies on an analytic transform of spatially defined antialiasing filters to an equivalent temporal domain filter bank.
@@
 First, a general analytical approach is introduced allowing the transform of an arbitrary spatial filter to an equivalent temporal filter set.
-From herein, subscript $x$ and $t$ distinguishes wether a filter is defined as a spatial or a temporal filter, respectively.
+From herein, subscript $x$ and $t$ distinguishes whether a filter is defined as a spatial or a temporal filter, respectively.
 
@@
 \end{equation}
-where $\ast_x$ denotes a circular convolution for a convex SSD contour or a linear convolution in case of an infinite long linear SSD.
+where $\ast_x$ denotes a circular convolution for a convex SSD contour or a linear convolution in case of an infinite, linear SSD.
 
@@
 
-\subsubsection{The exact transformation}
-The following transformation is allowed by the spatio-temporal structures of the conventional driving functions \eqref{eq:d_wfs_td}, in which the spatial and temporal dimensions are interconnected in the argument of a Dirac-delta, due to the wave propagation characteristics.
+\subsubsection{Exact transformation}
+The following transformation is allowed by the spatio-temporal structures of the driving functions \eqref{eq:d_wfs_td}, in which the spatial and temporal dimensions are interconnected in the argument of a Dirac-delta, due to the wave propagation characteristics.
 The main idea of the derivation is that by exploiting the sifting property of the Dirac-delta in the driving functions, both spatial and temporal convolutions \eqref{eq:spatial_conv} and \eqref{eq:temp_conv} can be evaluated, from which the temporal filter impulse responses can be expressed as the function of the spatial ones.
@@
     d'_t(s,t) = A^D(s) \, h_t \!\left(s,t- \tau(s) \right) \\
-    d'_t(s,t + \tau(s) ) = A^D(s) \, h_t \!\left(s,t\right).
+    d'_t(s,t + \tau(s) ) = A^D(s) \, h_t \!\left(s,t\right),
     \label{eq:temp_conv_eval}
 \end{align}
-In the second equation the time shift of $\tau(s)$ was applied for the sake of simplicity.
+with the second equation obtained by applying the time shift of $\tau(s)$ for the sake of later simplicity.
 
@@
 \begin{equation}
-    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \tau(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
+    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \tau(s_0) = -\frac{\hat{k}_t^P(s_0)}{c}.
 \end{equation}
-i.e. it is the tangential component of the local propagation vector.
+Here $\hat{k}_t^P(s_0)$ is the tangential component of the local propagation vector, defined as
+\begin{equation}
+    \hat{k}_t^P(s_0) = \mathbf{t}^{\mathrm{T}}(s_0) \hat{\vk}^P(s_0),
+\end{equation}
+with $\mathbf{t}^{\mathrm{T}}(s_0)$ denoting the unity long tangential vector of the SSD element at position $s_0$.
+
 With the above assumptions the integral \eqref{eq:spat_conv2} can be evaluated, yielding
@@
 
-Equation \eqref{eq:temporal_transform} can be directly expressed in the spectral domain by taking the Fourier transform of both sides, relating the frequency response of the spatial and the temporal filters.
+Equation \eqref{eq:temporal_transform} can be directly expressed in the spectral domain by taking the Fourier-transform of both sides, relating the frequency response of the spatial and the temporal filters.
 By denoting $\mathcal{F}\left( h_x(s)\right) = H_x(k_s)$ the corresponding transform is given by
@@
 
-Figure (a) shows the result of the synthesis, while Figure (b) illustrates the spectrum of the bandlimited, sampled driving functions.
+Figure \ref{Fig:symm_antialiasing} (a) shows the result of the synthesis, while Figure \ref{Fig:symm_antialiasing} (b) illustrates the spectrum of the bandlimited, sampled driving functions.
 \begin{figure}[h!]
@@
 In other positions of the listening area lateral aliasing wavefronts remain in the reproduced wave field, while the target, virtual wave front is bandlimited.
-This phenomenon can be easily understood by investigating the synthesis scenario in a geometrical manner:
+This phenomenon can be understood by investigating the synthesis scenario in a geometrical manner:
 
 Since the cutoff frequency of the antialiasing filter (Eq.
-\eqref{eq:cutoff_fr}) is inversely proportional to the tangential component of the virtual field on the SSD, therefore, in a circular array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly (i.e.
+\eqref{eq:cutoff_fr}) is inversely proportional to the tangential component of the virtual field on the SSD, in a circular array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly (i.e.
 where the tangential component of the local propagation vector is zero).
@@
 The direction of the line of aliasing-free synthesis is marked with a dashed arrow in the figure.
-This is in contrast with previous local WFS approaches, in which the synthesis is optimized in the proximity of a pre-defined reference position over a circular area.
+This is in contrast with previous LWFS approaches, in which the synthesis is optimized in the proximity of a pre-defined reference position over a circular area.
 
@@
 from which formulation it is apparent that in the frequency domain the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach, and the frequency dependent spatial window is given by $H_x\left(-k_t^P(s)\right)$:
-in the aspect of antialiasing filtering SSD positions where the local wavenumber vector is higher than the Nyquist wavenumber are highly attenuated, with the window width decreasing with increasing angular frequency.
+in the aspect of antialiasing filtering SSD positions where the local tangential wavenumber is higher than the Nyquist wavenumber are highly attenuated, with the window width decreasing with increasing angular frequency.
 \begin{figure}[]
@@
 \end{figure}
-The actual shape of the spatial windows are given by the wavenumber spectrum of the spatial lowpass filter $H_x(k_s)$, rescaled in terms of the local wavenumber vector.
+The actual shape of the spatial windows are given by the wavenumber spectrum of the spatial lowpass filter $H_x(k_s)$, rescaled in terms of the local tangential wavenumber.
 The set of window functions applied in the present simulation scenario are illustrated in Figure \ref{Fig:equivalent_windows}.
@@
 \end{equation}
-where $\hat{k}_{s,0}$ is the normalized center wavenumber and with
+with the normalized center wavenumber $\hat{k}_{s,0}$ and with
 \begin{equation}
@@
 \end{figure}
-The application of the above formulation with an arbitrarily chosen center wavenumber $\hat{k}_{s,0} = 0.5$ is depicted in Figure \ref{Fig:assymm_antialiasing}.
+The application of the above formulation with an arbitrarily chosen center wavenumber $\hat{k}_{s,0} = \nicefrac{1}{2}$ is depicted in Figure \ref{Fig:assymm_antialiasing}.
 Note that the wavenumber content of the original spatial lowpass filter is ,,steered'', so that the center frequency varies linearly with the angular frequency and the slope of the variation is given by the normalized center wavenumber.
-Obviously, this ,,steered'', frequency dependent band-pass filter theoretically also ensures non-overlapping spectra after the discretization process.
+This ,,steered'', frequency dependent band-pass filter theoretically also ensures non-overlapping spectra after the discretization process.
 
 From \eqref{eq:cutoff_asymm} it is apparent that in the present case the nearly fullband SSD element will be that, where the tangential local propagation vector coincides with the normalized center wavenumber, i.e.
-where $\hat{k}_t^P(s) = \hat{k}_{s,0} = 0.5$.
+where $\hat{k}_t^P(s) = \hat{k}_{s,0} = \nicefrac{1}{2}$.
 Again, the fullband SSD element is denoted by white dot in Figure \ref{Fig:assymm_antialiasing} (a).
@@
 \subsubsection{Application for Local Wave Field Synthesis}
-The findings of the previous subsections can be straightforwardly used in order to apply the above theory directly for Local Wave Field Synthesis.
+The findings of the previous subsections can be straightforwardly used in order to apply the above theory directly for LWFS.
 In this case a reference position $\vxref$ is prescribed inside the SSD, at which aliasing-free, amplitude and phase correct synthesis has to be ensured.
@@
     \end{center}
-    \caption{Spectrum of LWFS driving functions by direct modal bandlimitation with the reference position choosen at the center, $\vxref = \left[0,0,0\right]^{\mathrm{T}}$ (a) and on the left side, $\vxref = \left[0,1,0\right]^{\mathrm{T}}$ (b).
+    \caption{Spectrum of LWFS driving functions by direct modal bandlimitation with the reference position choosen at the center, $\vxref = \left[0,0\right]^{\mathrm{T}}$ (a) and on the left side, $\vxref = \left[0,1\right]^{\mathrm{T}}$ (b).
     }
@@
     \caption{Comparison of the proposed, temporal filtering-based LWFS approach with direct modal bandlimitation.
-    First row (a-d) depicts the synthesized field with temporal LWFS, Second row (e-h) depicts the synthesized field with modal bandlimitation and third row (i-l) compares the frequency response at the reference position.}
+    First row (a-d) depicts the synthesized field with temporal LWFS.
+Second row (e-h) depicts the synthesized field with modal bandlimitation and third row (i-l) compares the frequency response at the reference position.}
     \label{Fig:comparison}
@@
 
-Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.
+Finally, the performance of the proposed LWFS approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation \cite{hahn2022cylindrical}.
 \input{lwfs-spl.tex}
@@
 \begin{itemize}
-    \item Center: $\vxref = \left[0,0,0\right]^{\mathrm{T}}$
-    \item Left: $\vxref = \left[0,1,0\right]^{\mathrm{T}}$
-    \item Back: $\vxref = \left[-1,0,0\right]^{\mathrm{T}}$
-    \item Front: $\vxref = \left[1,0,0\right]^{\mathrm{T}}$
+    \item Center: $\vxref = \left[0,0\right]^{\mathrm{T}}$
+    \item Left: $\vxref = \left[0,1\right]^{\mathrm{T}}$
+    \item Front: $\vxref = \left[1,0\right]^{\mathrm{T}}$ 
+    \item Back: $\vxref = \left[-1,0\right]^{\mathrm{T}}$
 \end{itemize}
@@
 Figure \ref{Fig:nara_spectrum} already reflects the fact that the proposed temporal LWFS approach is an approximation of the reference solution, i.e. of the direct modal bandlimitation.
-It is verified that modal bandlimitation LWFS performs the same "steering" of the modal spectrum into the direction of the central wavenumber, realizing a freuqency dependent spatial band-pass filter.
+It is verified that modal bandlimitation LWFS performs the same steering strategy of the modal spectrum into the direction of the central wavenumber, realizing a frequency dependent spatial band-pass filter.
 
-Figure \ref{Fig:comparison} presents the comparison of the result of the two approaches via the synthesized field and the frequency response, each column illustrating a different reference position.
+Figure \ref{Fig:comparison} presents the comparison of the two approaches via the synthesized field and the frequency response, each column illustrating a different reference position.
 The first row (a-d) shows the synthesized field at the time instant of the plane wave pass-by through the reference position by implementing the proposed LWFS approach, with the second row (e-h) depicting the same result with using modal bandlimitation.
@@
 
-The figures reflects that both methods are capable of sufficient suppression of the aliasing wave fronts at the prescribed reference position in a qualitatively similar manner.
-The measured frequency responses show that the presented approach slightly suffers from ripples above the spatial aliasing frequency.
-This remaining aliasing artifact can be explained as the result of the approximations, introduced in the derivation of the temporal-to-spatial filter transform.
+The plots reflect that both methods are capable of sufficient suppression of the aliasing wave fronts at the prescribed reference position in a qualitatively similar manner.
+The frequency responses show that the presented approach slightly suffers from ripples above the spatial aliasing frequency.
+This remaining aliasing artifact can be explained as the result of the approximations, introduced in the derivation of the spatial-to-temporal filter transform.
 
@@
 The phenomena is explained by the spatial variation of the spatial aliasing frequency and the aliasing intensity, which has been already investigated in details in \cite{8611109} in a geometrical manner.
-The incorporation of this effect in the present antialiasing strategy is the subject of a further research. 
+The incorporation of this effect in the present antialiasing strategy is the subject of further research. 
 Yet, it has been already reported that choosing a non-critical modal bandwidth below the Nyquist wavenumber is an efficient strategy to avoid these remaining aliasing wavefront \cite{Hahn17:EUSIPCO}.
@@
 
-The present contribution discussed a novel local Wave Field Synthesis approach, allowing an increased synthesis accuracy in the proximity of a reference position when a sparse SSD is applied for sound field reproduction.
+The present contribution discussed a novel LWFS approach, allowing an increased synthesis accuracy in the proximity of a reference position when a discrete SSD is applied for sound field reproduction.
 The approach relies on a filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
-Local WFS is achieved by spatial bandlimiting of the SSD driving function to the Nyquist wavenumber, achieved by suitable spatial filtering.
+LWFS is achieved by spatially bandlimiting of the SSD driving function to the Nyquist wavenumber, achieved by suitable spatial filtering.
 By transforming the spatial antialiasing filters to a temporal filter bank, LWFS can be performed by the simple temporal bandlimitation of the SSD driving signals.
 
-It was demonstrated via numerical simulations that the approach is capable of the suppression of aliasing wavefronts along a straight line/ray, passing through a predefined the reference position.
+It was demonstrated via numerical simulations that the approach is capable of the suppression of aliasing wavefronts along a straight line/ray, passing through a predefined reference position.
 The direction of antialiasing synthesis can be set by adjusting the center wavenumber of the antialiasing spatial band-pass filter.
-The performance of the presetned approach was compared with LWFS by direct modal bandlimitation taken as a direct, reference solution.
-It was shown that temporal LWFS gives a feasible approximation for the reference one, while being a more robust approach with less computational demand, allowing even real-time implementations. 
-Furthermore, altough the proposed approach was validated via the example of a virtual plane wave, the technique is capable of the aliasing-free synthesis of an arbitrary simple virtual field model.
+The performance of the presented approach was compared with LWFS by direct modal bandlimitation taken as reference solution.
+It was shown that temporal LWFS gives a feasible approximation for the reference one, while being a more robust approach with less computational demand, allowing real-time implementations. 
+Furthermore, although the proposed approach was validated via the example of a virtual plane wave, the technique is capable of the aliasing-free synthesis of an arbitrary simple virtual field model.
 
-It was demonstrated that both approaches suffer for remaining aliasing artifacts in off-center reference positions that's suppression is the topic of further research.
+It was demonstrated that both approaches suffer for remaining aliasing artifacts in off-center reference positions. 
+The further mitigation of the off-center aliasing waves is the topic of further research.
 
-Finally, as an important limitation of the proposed technique it has to be pointed out, that since the proposed approach bandlimits the driving signals as the function of the local propagation direction of the virtual field on the SSD, therefore, the overall synthesis bandlimit varies with the virtual source direction/position.
+Finally, as an important limitation of the proposed technique it has to be pointed out, that the proposed approach bandlimits the driving signals as the function of the local propagation direction of the virtual field on the SSD, therefore, the overall synthesis bandlimit varies with the virtual source direction/position.
 This can result in enhanced artifacts in case of a non-stationary virtual field, e.g. in case of the synthesis of a moving source.

### 2023-08-14 paper/main.tex
final_paper

@@
 \usepackage{overpic,subfigure, tikz}
+
+\usepackage{amsmath}
+\usepackage{bm}
+\usepackage{tkz-euclide}
+\usetikzlibrary{shapes,snakes}
+% we should use matplotlib colors:
+\definecolor{C0}{HTML}{1f77b4}
+\definecolor{C1}{HTML}{ff7f0e}
+\definecolor{C7}{HTML}{7f7f7f}
+
+\makeatletter
+\newcommand{\tikzAngleOfLine}{\tikz@AngleOfLine}
+\def\tikz@AngleOfLine(#1)(#2)#3{%
+  \pgfmathanglebetweenpoints{%
+    \pgfpointanchor{#1}{center}}{%
+    \pgfpointanchor{#2}{center}}
+  \pgfmathsetmacro{#3}{\pgfmathresult}%
+}
+\makeatother
+\tikzset{mark coordinate/.style={inner sep=0pt,
+                                   outer sep=0pt,
+                                   minimum size=3pt,
+                                   fill=#1,
+                                   circle}
+                                   }
 
@@
 The latter approach is implemented by \cite{hahn2022cylindrical}, and will serve as a reference solution in the following investigation.
-However, the modal bandlimitation solution is available only for plane wave and point source virtual source models, at the cost of increased computational complexity.
+However, the modal bandlimitation solution is available so far only for plane wave and point source virtual source models---where the driving functions can be derived analytically---, at the cost of increased computational complexity.
 
@@
 \end{equation}
-with $\mathbf{t}^{\mathrm{T}}(s_0)$ denoting the unity long tangential vector of the SSD element at position $s_0$.
+with $\mathbf{t}^{\mathrm{T}}(s_0)$ denoting the unity long tangential vector of the SSD element at position $s_0$, as illustrated in Figure \ref{fig:tangential_local_prop_vec}.
+
+\begin{figure}
+    \begin{center}
+        \begin{tikzpicture}[scale=1.2 ]
+    \begin{scope}
+
+    % these coordinates / parameters can be freely chosen:
+    \coordinate (x0) at (-1.5,0);  % determines the radius of SSD
+    \coordinate (xPS) at (-3.5,2);  % make sure that point source is outside of SSD
+    % for wave pattern 'snake=expanding waves' stuff
+    \def \segmentangle {30};  % opening angle of wave pattern in deg
+    \def \segmentlength {5};  % somehow determines the wavelength
+    \def \wavepatternlength {3.5};  % determines how far the wave propagates into the SSD
+
+    % ---> change with care:
+    \coordinate (origin) at (0,0);
+    % SSD circle
+    \node[name path=FullSSDCircle, draw, thin, color=black, circle through=(x0)] (FullSSDCircleNode) at (origin) {};
+    % wave pattern to x0
+    \draw[snake=expanding waves, segment angle=\segmentangle, segment length=\segmentlength, color=C7!33] (xPS)  -- (x0);
+    % wave pattern additionally into SSD, length is defined with \wavepatternlength
+    \tikzAngleOfLine(x0)(xPS){\angle};
+    \draw[snake=expanding waves, segment angle=\segmentangle, segment length=\segmentlength, color=C7!33] (xPS)  -- ++(\angle:-\wavepatternlength);
+    % line from point source to specific SSD point
+    \draw[-, thick, C7] (xPS) -- (x0) node[left, black]{$\bm{x}_0$};
+    % normal / tangent vectors of SSD at x0
+    \tikzAngleOfLine(origin)(x0){\angle};
+    \draw[->, >=stealth', thick, C0] (x0) -- ++(\angle:-1) node[right]{$\bm{n}$};
+    \draw[->, >=stealth', thick, C1] (x0) -- ++(\angle-90:-1) node[below]{$\bm{t}$};
+    % normal / tangent vectors of sound field at x0
+    \tikzAngleOfLine(x0)(xPS){\angle};
+    \draw[->, >=stealth', thick, C1] (x0) -- ++(\angle:-1) node[right]{$\hat{\bm{k}}$};
+    \draw[->, >=stealth', thick, C0] (x0) -- ++(\angle+90:-1) node[right]{$\hat{\bm{k}}_t$};
+    % black dots indicating positions of point source and specific SSD point
+    \draw[thick] (xPS) coordinate [mark coordinate=black, label=left:{$\bm{x}_\text{PS}$}];
+    \draw[thick] (x0) coordinate [mark coordinate=black];
+    % <---
+
+    % !!!
+    % these projection lines are hard coded for (x0) at (-1.5,0); (xPS) at (-3.5,2);
+    \draw[dashed, C0] (-0.79,0.7) -- (-0.79,0) node[below] {$\hat{k}_t$};
+    \draw[dashed, C1] (-0.8,-0.7) -- (-1.5,-0.7) node[left] {$\hat{k}_t$};
+
+    \end{scope}
+    \end{tikzpicture}
+\end{center}
+\caption{Illustration for the tangential component of the local propagation vector in the exemplary case of the field of a virtual point source, located at $\vx_{\mathrm{PS}}$ and applying a circular SSD.
+On the figure $\bm{t}$ and $\bm{n}$ denote the tangential and normal vector of the SSD respectively, $\hat{\bm{k}}_t$ denotes the tangential vector of the sound sound field and $\hat{k}_t$ denote the tangential component of the local propagation vector ($\hat{\bm{k}}$) at the SSD position $\vxo$.}
+\label{fig:tangential_local_prop_vec}
+\end{figure}
 
@@
 From general WFS theory it is known that the fullband SSD element will dominate the synthesized wavefront (i.e.
-will serve as a stationary SSD position) for spatial positions along a straight line crossing the actual SSD element into the direction of the local propagation vector.
+will serve as a stationary SSD position) for spatial positions along a straight line crossing the actual SSD element into the direction of the local propagation vector \cite{Firtha2019phd}.
 Therefore, the present antialiasing strategy ensures aliasing-free synthesis along a straight line for which the fullband SSD element is the stationary secondary source.
